---
title: "Datapreparation TRACE dataset: calculate effect sizes and add QA scores"
author: "Valeria Bonapersona & Milou Sep"
date: "March 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


## Preparation of the environment
```{r setup}
rm(list = ls()) #clean environment
# libraries
library(metafor) # for effect size estimation
library(dplyr) #for general functions
# library(osfr)
library(readxl)
```

```{r}
data<-readRDS("processed_data/TRACErecoded.RDS") # contains only included, recoded, data 
str(data)
```

## Correction for multiple use control group

### Merge ID's of experimental and control groups.
```{r}
data1 <- data %>% mutate(
  new.idPTSD = as.factor(paste(PMID,idPTSD, sep=".")),
  new.idHC = as.factor(paste(PMID,idHC, sep=".")),
  id_combination = as.factor(paste(new.idPTSD, new.idHC, sep=".")))
# for checking (should be NA, if both missing excluded in dataset)
data1 %>% filter(is.na(semPTSD) & is.na(sdPTSD)) #%>% View()
data1 %>% filter(is.na(semHC) & is.na(sdHC)) #%>% View()
```

### Check which control groups are used multiple times
```{r}
reused_controls <- data1 %>%
  select(new.idPTSD, new.idHC, id_combination)%>%
   group_by(new.idHC) %>% #for each control groups
  summarise(used=length(unique(id_combination)))%>%  # count the amount of unique id combinations
  filter(used>1) # show control groups in which a unique combination is precent more than once
reused_controls # 10 control groups are used in multiple unique id_combinations # 18.3.19 11 control grousp used multiple times # 8.4.21 66 are reused
#20.4.21 na toevoegen PMID zijn er 21 reused.

# NB: used is here het aantal experimentale groupen waarmee de controle group vergeleken is.. (niet het aantal measures oid, dus vergeleken met 1 exp group, op 10 maten, used =1)

#' Check results
# data1 %>% filter(new.idHC%in%reused_controls$new.idHC) %>% 
#   # select(PMID, idHC, new.idHC, used, id_combination) %>% 
#   # arrange(PMID, new.idHC) %>% 
#   View()


#' add to dataframe
# left_join(data1,reused_controls, by="new.idHC") %>% View() # yes correct (old code was not)

left_join(data1,reused_controls, by="new.idHC") -> data2

# data1 %>% mutate(
#   used = ifelse(new.idHC%in%reused_controls$new.idHC, reused_controls$used, NA )
#   
# )%>% filter(!is.na(used)) %>% View()

#' Recalculate n's
data2 %>% mutate(
  nHC_corrected = ifelse(!is.na(used), nHC/used, nHC)
) ->data3

# data1$nHC_corrected<-ifelse(!is.na(data1$used), data1$nHC/data1$used, data1$nHC)

#' Check if the effects are correct.. yes
data3 %>% 
  filter(new.idHC %in% reused_controls$new.idHC)  %>% 
  select(nHC, nHC_corrected, used) %>% head()
#' round
data3$nHC<-round(data3$nHC_corrected)
```


## Calculate SD from SEM
```{r}
data3$sdPTSD <- ifelse(is.na(data3$sdPTSD), (data3$semPTSD * sqrt(data3$nPTSD)), data3$sdPTSD)
data3$sdHC <- ifelse(is.na(data3$sdHC), (data3$semHC * sqrt(data3$nHC)), data3$sdHC)
``` 

## Check Missing values (should be none)
```{r}
#' Sample sizes ok
which(is.na(data3$nPTSD))
which(is.na(data3$nHC))
#' sd ok
which(is.na(data3$sdPTSD))
which(is.na(data3$sdHC))

#' #' Missing values SD? Original datafile checked: 5 papers don't report sem or sd: PMID: 7654154, 8731522, 9821567, 17392739, 27297027
#' unique(data[which(is.na(data$sdHC)),"PMID"]) 
#' #' Theses values correspond with original datafile, and are excluded from further analysis
#' dat %>% filter(!is.na(sdC)) -> dat
data3 %>% select(-c(semPTSD, semHC, idPTSD, idHC, used, nHC_corrected)) -> data4 # Remove unnecessary columns

#' Missingvalues are checked again, should be non.. # update 8.4.21 -> there are missings.. as shock, time res.sus split are still in data
# which(is.na(data1)) 

data4 %>% select(!c("shocks.num", "shocks.amp", "time","res.sus.split")) %>% filter(!(is.na(.))) %>% nrow() # is idem als total  (=1643)

#' update 19.3.19: na toevoeging "keyfinding", sommmige na, anders niet.
# head(is.na(data1)) 
```

## Calculation of effect sizes and checks
```{r}
data5 <- escalc(
  m1i = meanPTSD, sd1i = as.numeric(sdPTSD), n1i = nPTSD, 
              m2i = meanHC, sd2i = as.numeric(sdHC), n2i = nHC, 
              measure = "SMD", #method = "HE",  # calc hedge's G
              data = data4)
```

## Recode Effect sizes in same direction (higher score = better performance)
NB variable recode contains extinction recode codes were higher scores (higher anxiety) is coded as more memory persistence (would correspond to less extinction)

```{r}
#' Based on recode variable, which is specified in "Trace_methode_codes.csv"
# data5$yi <- data5$yi * data5$recode
data5$yi <- data5$yi * data5$recode.for.ext

#' INTERPRETATION: Viechtbauer, W. (2010). Conducting Meta-Analyses in R with the metafor Package. Journal of Statistical Software, 1–48. Page 7
#' "SMD": The standardized mean difference is equal to (m1i m2i)/spi
#' In the calulations above 1 = ptsd en 2 = control; therefore positive effect size = PTSD more, negative effectsize is HC more 

```

## add unique id's
```{r}
data5$each <- c(1:nrow(data5)) 
```

# Add QA info
```{r}
readRDS("processed_data/TRACE_QA_animal.RData") %>% select(PMID, QA_score)->QA.A
readRDS("processed_data/TRACE_QA_human.RData") %>% select(PMID, QA_score)->QA.H

bind_rows(QA.A, QA.H) %>% mutate(PMID = as.character(PMID))->QA

left_join(data5, QA, by="PMID") %>% droplevels() -> data6 #drop missing levels & Remove 'unique id combination' variable (not needed anymore)
```

#for checking
```{r eval=FALSE, include=FALSE}
data6 %>% select(type, phase, valence, recode, cuectx) %>% is.na() %>% any() # must be false (if method codes are added correctly)
```

# Save resulting dataset --------------------------------------------------
```{r}
saveRDS(data6, file = "processed_data/TRACEprepared.RData") #save
```
