---
title: "Descriptives"
author: "Milou Sep"
date: "4/15/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Environment Preparation
```{r setup, include=FALSE}
rm(list = ls()) #clean environment
library(dplyr)
library(arsenal) # for tables
```

# Recode Data labels
A= non-exposed vs trauma-exposed PTSD (human); B=non-exposed vs trauma exposed no PTSD (human); C=trauma-exposed (noPTSD) vs trauma-exposed PTSD (human); D=non-exposed vs trauma-exposed (no PTSD checked) (animal); E=non-exposed vs trauma-exposed PTSD (animal); F=trauma-exposed (no ptsd) vs trauma-exposed PTSD (animal)
```{r}
data<-readRDS("processed_data/data.explore.rds")

data %>% 
  mutate(
    # recode comparison typs
    Comparison = case_when(
      comparison == "A" ~ "non-exposed vs PTSD",
      comparison == "B" ~ "non-exposed vs trauma-exposed",
      comparison == "C" ~ "trauma-exposed vs PTSD",
      comparison == "D" ~ "non-exposed vs trauma-exposed",
      comparison == "E" ~ "non-exposed vs PTSD",
      comparison == "F" ~"trauma-exposed vs PTSD"),
    subject.cat=factor(subject.cat, levels = c("Human", "Animal"), labels = c("Clinical", "Preclinical")),
    # full descriptions ptsd models animals
    ptsd.type = recode(ptsd.type,
                       UWT = "Under Water Trauma",
                       FS = "Footshock",
                       SPS = "Single Prolonged Stress",
                       PSS = "Predator Scent Stress",
                       RS = "Restrained Stress",
                       SD = "Social Defeat")
  ) %>%  
  # select independent PTSD groups
  distinct(new.idPTSD, .keep_all = TRUE) %>%
  droplevels()->df.filterd
```

# Set table controls
```{r}
# https://rdrr.io/cran/arsenal/man/tableby.control.html
mycontrols  <- tableby.control( test=F, total=F,na.rm=T,
                                numeric.stats=c( "meansd","range","Nmiss"),
                                cat.stats = c("countpct", "Nmiss"),
                                ord.stats= c("countpct","Nmiss"),
                                stats.labels=list(Nmiss='Missing', Nmiss2='Missing', countpct="test",
                                                  meansd="Mean (SD)", range="Range"),
                                pfootnote=TRUE,
                                cat.simplify = F, numeric.simplify = T, ordered.simplify = T,
                                digits=2,
                                digits.p=2,
                                digits.count=0,
                                digits.pct=0 )
```

```{r}
names(df.filterd)
```

# Table with comparison types
```{r}
df.filterd %>%
  tableby(subject.cat ~ Comparison,., control = mycontrols) %>%
  write2word(., "descriptives.comparison.doc", title="Characteristics Included studies",
             labelTranslations = c(Comparison="Experiment: Comparison Type"))
```

# Table variables in clinical and preclinical data
```{r}
df.filterd %>%
  filter(comparison != "B") %>%  # excluded comparison B from human dataset
  droplevels() %>%
  tableby(
    subject.cat ~ control.type + time.since.trauma + rhythm + sex + age + phase + valence + cue.context + information.type,
    data=., control = mycontrols
  ) ->table.combi
```

```{r results="asis"}
table.combi %>% summary(., text=T) 
```

All to pseudo-years: recode time in human, rat and mice
- in adulthood: 11.8 rat days = 1 human year [https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3733029/]
- in adulthood: 2.60 mice day = 1 human year  [https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3733029/]
```{r}
combi.table.labels <-c(
  control.type	= "Experiment: Control Type",
  rhythm = "Experiment: Day/Night Phase",
  time.since.trauma = "Experiment: Time since trauma, (expressed in human years)",
  sex = "Subject: Sex",
  age = "Subject: Age",
  phase = "Task: phase",
  valence = "Task: Valence",
  cue.context = "Task: Cue / Context",
  information.type = "Task: information type")
```

Export to CSV
```{r eval=FALSE, include=FALSE}
table.combi %>% summary(., text=NULL) %>% as.data.frame() %>% write.csv2(.,"results/descriptives.csv")
```

Export to word
Note, if export does not work: uncheck the option "Tools > Global Options > R Markdown > Show output inline for all R Markdown documents."
```{r}
write2word(table.combi, "descriptives.combined.doc", title="Characteristics Included studies",
           labelTranslations = combi.table.labels)
```

# Tables with unique clinical or preclinial variables
Set labels split tables
```{r}
split.table.labels<-c(
  population="Subject: Population",
  sample = "Subject: Sample",
  ptsd.type = "Subject: Trauma Sequelae",
  measure = "Task: Measure")
```
## Clinical
```{r}
df.filterd %>% 
  filter(subject.cat == "Clinical") %>% 
  filter(comparison != "B") %>%  # excluded comparison B from human dataset
  droplevels() %>%
  tableby(~ population + # almost similar as sample
            sample + ptsd.type + measure, data=., control = mycontrols) ->table.clinical

table.clinical%>% summary(.,text=T)

write2word(table.clinical, "descriptives.clinical.doc", title="Characteristics Included clinical studies",
           labelTranslations = split.table.labels)
```
## Preclinical
```{r}
df.filterd %>% 
  filter(subject.cat == "Preclinical") %>% 
  droplevels() %>%
  tableby(~ population + sample + ptsd.type + measure, data=., control = mycontrols) ->table.preclinical

table.preclinical%>% summary(.,text=T)

write2word(table.preclinical, "descriptives.preclinical.doc", title="Characteristics Included preclinical studies",
           labelTranslations = split.table.labels)
```