---
title: "Flowchart"
author: "Milou Sep"
date: "2/4/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls()) #clean environment
# load files from OSF
library(osfr)
# Authenticate to OSF (see: http://centerforopenscience.github.io/osfr/articles/auth.html). Via osf_auth("PAT") in the commentline. (note PAT can be derived from OSF)
library(readxl)
library(dplyr)
# for flow chart
library(grid)
library(Gmisc)
```

### Download local copy of required data files from OSF 
```{r eval=FALSE, include=FALSE}
osf_retrieve_file("7k6wh") %>% osf_download(path = "data", conflicts="overwrite") # dataset search 1
osf_retrieve_file("7kdmu") %>% osf_download(path = "data", conflicts="overwrite") # human search 2
osf_retrieve_file("fs2gq") %>% osf_download(path = "data", conflicts="overwrite") # animal search 2

osf_retrieve_file("nqgaf") %>% osf_download(path = "data", conflicts="overwrite") # human search 3
osf_retrieve_file("s3ake") %>% osf_download(path = "data", conflicts="overwrite") # animal search 3

osf_retrieve_file("tqmwb") %>% osf_download(path = "data", conflicts="overwrite") # screening & data extraction S1

osf_retrieve_file("pu6bf") %>% osf_download(path = "data", conflicts="overwrite")  #abstract screening search2 SH
osf_retrieve_file("56fyu") %>% osf_download(path = "data", conflicts="overwrite")  #abstract screening search2 MS

osf_retrieve_file("ugyrp") %>% osf_download(path = "data", conflicts="overwrite") # discussed animal
osf_retrieve_file("kve78") %>% osf_download(path = "data", conflicts="overwrite") # discussed human data

osf_retrieve_file("xmua6") %>% osf_download(path = "data", conflicts="overwrite") # full text checks animal animal
osf_retrieve_file("ce35r") %>% osf_download(path = "data", conflicts="overwrite") # full text checks human animal

osf_retrieve_file("m9rey") %>% osf_download(path = "data", conflicts="overwrite") # inclusion s2 (screening) animal
osf_retrieve_file("fe5sh") %>% osf_download(path = "data", conflicts="overwrite") # inclusion s2 (screening) human
osf_retrieve_file("xqpm3") %>% osf_download(path = "data", conflicts="overwrite") # screening & data extraction S2

osf_retrieve_file("famr7") %>% osf_download(path = "data", conflicts="overwrite")
osf_retrieve_file("wbrcm") %>% osf_download(path = "data", conflicts="overwrite") # screening & data extraction S1

```

# Load data files in environment
```{r}
# PIMD hits
search1_animal <- read_excel("data/Review PTSD Cognition AbstractScreening_Overeenstemming EG & MS v15.11.2016.xlsx", sheet = "Animal hits n=178 SSv18.10.2016", col_types = "numeric")
search1_human <- read_excel("data/Review PTSD Cognition AbstractScreening_Overeenstemming EG & MS v15.11.2016.xlsx",  sheet = "Human Hits n=292 SSv12.10.2016", col_types = "numeric")

animal_search2 <- read.table("data/pubmed_result_search2_animal 6.1.20.txt",  quote="\"", comment.char="")
human_search2<- read.table("data/pubmed_result_search2_human 6.1.20.txt", quote="\"", comment.char="")

animal_search3 <- read.table("data/pmid.animal.s3.learn.22.5.20.txt",  quote="\"", comment.char="")
human_search3<- read.table("data/pmid.human.s3.learn.22.5.20.txt", quote="\"", comment.char="")

# Screening
SH_animal.S2 <- read_excel("data/TRACE_screening_search2_SH.xlsx", sheet = "screening search 2 animal") %>% filter(!is.na(Reference_PMID))
MS_animal.S2 <- read_excel("data/TRACE_screening_search2_MS.xlsx", sheet = "screening search 2 animal")
SH_human.S2 <- read_excel("data/TRACE_screening_search2_SH.xlsx", sheet = "screening search 2 human") %>% filter(!is.na(Reference_PMID))
MS_human.S2 <- read_excel("data/TRACE_screening_search2_MS.xlsx", sheet = "screening search 2 human")

animal_discussed_s2 <- read.csv2("data/inconsistencies_animal_s2_SH.csv")
human_discussed_s2 <- read.csv2("data/inconsistencies_human_s2_SH.csv")

full_text_check_s2_animal <- read.csv2("data/required_full_checks_animal_s2_MS.csv")
full_text_check_s2_human <- read.csv2("data/required_full_checks_human_s2_SH.csv")

animal_included_s2 <- read.csv2("data/animal_inclusions_s2.csv", na.strings = c(" ", "-")) 
human_included_s2 <- read.csv2("data/human_inclusions_s2.csv", na.strings = c(" ", "-")) 

s3.animal <- read_excel("data/Checked_TRACE_screening_search3_MS_EG.xlsx", sheet = "full.text.screening.s3.animal") %>% filter(!is.na(PMID))
s3.human <- read_excel("data/Checked_TRACE_screening_search3_MS_EG.xlsx", sheet = "full.text.screening.s3.human") %>% filter(!is.na(PMID))

# Data extraction
read_excel("data/TRACE data_collection_search1.xlsx", na = c(" ", "-")) -> data.s1
read_excel("data/TRACE data_collection_search2.xlsx", sheet = "animal_inclusions_s2")->data.s2.animal
read_excel("data/TRACE data_collection_search2.xlsx", sheet = "human_inclusions_s2")->data.s2.human
read_excel("data/TRACE_data_collection_search3.xlsx", sheet = "animal.inclusions.s3")->data.s3.animal
read_excel("data/TRACE_data_collection_search3.xlsx", sheet = "human.inclusions.s3")->data.s3.human

# Analyses
readRDS("processed_data/TRACEprepared.RData")->dataset.prep # This is the output of `prepare_effect_size_QA.rmd`, see README file

readRDS("processed_data/clinical.data.metaregression.RDS") -> metaregression.clinical # output analyses script
readRDS("processed_data/preclinical.data.metaregression.RDS") -> metaregression.preclinical

readRDS("processed_data/clinical.data.explorative.RDS") -> explorative.clinical # output exploratory analyses script
readRDS("processed_data/preclinical.data.explorative.RDS") -> explorative.preclinical 
```


# Search

## Compare PMIDs in search 1 and 2 of trace & remove duplicates code to remove duplicates from search 2 in TRACE project
 
### Get number of unique PMIDs from search 1
```{r warning=FALSE}
search1_animal %>% pull(PMID) %>% unique() %>% .[.!=178] %>% .[!is.na(.)] -> search1_animal_uPMID
# remove last 2 items in vector (these are not PMIDs, but counting/notes)
n.s1.A = length(search1_animal_uPMID) #178
n.s1.A
```

```{r warning=FALSE}
search1_human %>% pull(`PMID (op alfabet)`) %>% unique() %>% .[.!=292] %>% .[!is.na(.)] -> search1_human_uPMID
# remove last 2 items in vector (these are not PMIDs, but counting/notes)
n.s1.H = length(search1_human_uPMID) #292
n.s1.H
```


## compare results search 1 and 2

### Compare animal hits & and save unique id's to csv
```{r }
animal_search2[!animal_search2$V1 %in% search1_animal_uPMID,] -> animal_search2_uniq
n.s2.A = length(animal_search2_uniq)
# write.table(animal_search2_uniq, file = "animal_search2_unique.csv", sep = ';', row.names = F)
n.s2.A
```

### Compare human hits & and save unique id's to csv
```{r}
human_search2[!human_search2$V1 %in% search1_human_uPMID,] -> human_search2_uniq # "select the hits of search 2 that are NOT in search 1"
n.s2.H = length(human_search2_uniq)
# write.table(human_search2_uniq, file = "human_search2_unique.csv", sep = ';', row.names = F)
n.s2.H
```


## compare PMIDs in search 1,2,3

### Compare human hits 
```{r }
all(search1_human %in% human_search2$V1) # All items in search 1 are also in search 2
human_search3[!human_search3$V1 %in% human_search2$V1,]  -> unique.search3.human # therefore search 3 compared to search 2
n.s3.H = length(unique.search3.human)
# write.table(unique.search3.human, file = "human_search3_unique.csv", sep = ';', row.names = F)
n.s3.H
```

### Compare animal hits 
```{r }
all(search1_animal %in% animal_search2$V1) # All items in search 1 are also in search 2
animal_search3[!animal_search3$V1 %in% animal_search2$V1,]  -> unique.search3.animal # therefore search 3 compared to search 2
n.s3.A = length(unique.search3.animal)
 # write.table(unique.search3.animal, file = "animal_search3_unique.csv", sep = ';', row.names = F)
n.s3.A
```

# Collect Unique PMID screening search 1, 2 and 3 (n=1653)
```{r }
screened_articles <- c(search1_animal_uPMID, search1_human_uPMID, animal_search2_uniq, human_search2_uniq, unique.search3.animal, unique.search3.human)
unique_screened_articles <- unique(screened_articles) 
length(unique_screened_articles) #1653
 write.csv2(unique_screened_articles, 'processed_data/unique_screened_articles.csv')
```

## Conclusions:
### Total unique animal papers screened: 178 (S1) + 114 (S2) + 254 (S3)
```{r}
c(search1_animal_uPMID,  animal_search2_uniq, unique.search3.animal) -> screened_animal_articles
length(unique(screened_animal_articles)) == length((screened_animal_articles))
write.csv2(screened_animal_articles, 'processed_data/unique_screened_animal_articles.csv')

length((screened_animal_articles)) #546
total.screened.preclinical = n.s1.A + n.s2.A + n.s3.A
total.screened.preclinical
length((screened_animal_articles)) == total.screened.preclinical
```


### Total unique human papers screened: 292 (S1) + 142 (S2) + 681 (S3)
```{r}
c( search1_human_uPMID, human_search2_uniq, unique.search3.human) -> screened_human_articles
length(unique(screened_human_articles)) == length((screened_human_articles))
write.csv2(screened_human_articles, 'processed_data/unique_screened_human_articles.csv')
length((screened_human_articles)) #1115

total.screened.clinical = n.s1.H + n.s2.H + n.s3.H
total.screened.clinical
```

### Total unique screened:
```{r}
length(screened_articles) #1661 Total screened animal + human
length(unique_screened_articles) #1653 NOTE, Total unique screened animal + human is lower
length(screened_articles) - length(unique_screened_articles) # 8 screened articles where returned by both human and animal search strings
```

#### REF list. NB to create the reference list, there PMIDs were used for reversed PMID search in pubmed. This returened n=1652 unique (animal + human) papers. Note that is 1 less then number above. Inspection of the screening documents showed that one animal paper (from search 3) was linked to 2 PMIDs (31540952 and 31527186; see https://osf.io/famr7).
```{r eval=FALSE, include=FALSE}
osf_retrieve_file("f82as") %>% osf_download(path = "data", conflicts="overwrite") # dataset search 1
library(readr)
total_screening_pubmed_return <-read_csv2("data/References_screened_articles_TRACE.csv")
# total_screening_pubmed_return %>% head()
screened_articles[which(!screened_articles %in% total_screening_pubmed_return$PMID)]
#PMID 31540952 not returned by pubmed.

# Was in animal search 3:
31540952 %in% search1_animal
31540952 %in% animal_search2_uniq
31540952 %in% unique.search3.animal # in search 3
# for details see: https://osf.io/famr7
```


# Screening

## S1 screening

### Post-screeing inclusions and exclusions 
(Note, indicated in flowchart as "excluded in full-text screening")
```{r}
# str(data.s1)
data.s1 %>%  
  filter(`Screening_AbstractScreening_EG (1=include; 0 = exclude)` == 1 | `Screening_AbstractScreening_MS (1=include; 0 = exclude)` ==1) %>% 
    group_by(subject=`Screening_Human (1) of Animal (2)`) %>%
    distinct(Reference_PMID) %>% tally() ->s1.n.post.screening
s1.n.post.screening # split for clinical and preclinical
```

```{r}
s1.n.post.screening[1,2] + s1.n.post.screening[2,2] # clinical and preclinical together
# 157 + 87
```

### Data included for extraction 
(Note, indicated in flowchart as "included after full text screening")
```{r}
 # glimpse(data.s1)
data.s1 %>% 
  filter(inclusion == 1) %>% 
  group_by(subject=`Screening_Human (1) of Animal (2)`) %>%
  select(subject,Reference_PMID) %>% 
  distinct(Reference_PMID) %>% tally() -> s1.n.in.data
s1.n.in.data
```



## S2 screening
 
### Resolve inconsistencies in screening S2 
Note, not required for flow chart, therefor all three code blocks set to eval=F and include=F.
#### Step 1 check inconsistencies in abstract screening
```{r eval=FALSE, include=FALSE}
# remove rows with all NA's in screening SH
SH_animal.S2[rowSums(is.na(SH_animal.S2)) != ncol(SH_animal.S2), ]->SH_animal.S2
SH_human.S2[rowSums(is.na(SH_human.S2)) != ncol(SH_human.S2), ]->SH_human.S2

# make unique column names
colnames(SH_animal.S2) <- paste(colnames(SH_animal.S2),"SH", sep = "_")
colnames(MS_animal.S2) <- paste(colnames(MS_animal.S2),"MS", sep = "_")

colnames(SH_human.S2) <- paste(colnames(SH_human.S2),"SH", sep = "_")
colnames(MS_human.S2) <- paste(colnames(MS_human.S2),"MS", sep = "_")


# order animal data by PMID 
SH_animal.S2 %>% arrange(Reference_PMID_SH) -> SH_animal.S22
MS_animal.S2 %>% arrange(Reference_PMID_MS) -> MS_animal.S22

# check if ordering is the same:
all.equal(SH_animal.S22$Reference_PMID_SH, MS_animal.S22$Reference_PMID_MS)

# order human data by PMID 
SH_human.S2 %>% arrange(Reference_PMID_SH)->SH_human.S22
MS_human.S2 %>% arrange(Reference_PMID_MS)->MS_human.S22
# check if ordering is the same:
all.equal(SH_human.S22$Reference_PMID_SH,MS_human.S22$Reference_PMID_MS)

# merge data
cbind(SH_animal.S22, MS_animal.S22)->animal
cbind(SH_human.S22, MS_human.S22)->human

# select only PMID & ref.
# human %>% select(Reference_PMID_SH, inclusion_SH, Reference_PMID_MS, inclusion_MS) ->df.h
# animal %>% select(Reference_PMID_SH, Inclusion_SH, Reference_PMID_MS, inclusion_MS) ->df.a

# recode to same scale: 1=inclusion; 0=exclusion; ?=full text check needed
human %>% mutate(
  inclusion_MS=
    case_when(
      inclusion_MS==1 ~"yes",
      inclusion_MS==0 ~"no",
      grepl("?",inclusion_MS, fixed = T) ~ '?')
)->human_recoded

animal %>% mutate(
  inclusion_MS=
    case_when(
      inclusion_MS==1 ~"yes",
      inclusion_MS==0 ~"no",
      grepl("?",inclusion_MS, fixed = T) ~ '?')
) ->animal_recoded


# select equal rows
animal_recoded %>% mutate(
  conclusion1= case_when(
    # Inclusion_SH == '?' ~ 'full_text_check',
    # Inclusion_MS == '?' ~ 'full_text_check',
    (Reference_PMID_SH!=Reference_PMID_MS) ~'PMIDincor',
    # (Reference_PMID_SH==Reference_PMID_MS) & Inclusion_SH != '?' & (Inclusion_SH == inclusion_MS) ~ 'equal',
    (Reference_PMID_SH==Reference_PMID_MS) & (Inclusion_SH == inclusion_MS) ~ 'same',
    (Reference_PMID_SH==Reference_PMID_MS) & (Inclusion_SH != inclusion_MS) ~ 'discuss'
  )
)->animal_recoded2 

human_recoded %>% mutate(
  conclusion1= case_when(
    (Reference_PMID_SH!=Reference_PMID_MS) ~'PMIDincor',
    (Reference_PMID_SH==Reference_PMID_MS) &  (inclusion_SH == inclusion_MS) ~ 'same',
    # (Reference_PMID_SH==Reference_PMID_MS) & (inclusion_SH != '?' | inclusion_MS!="?") & (inclusion_SH == inclusion_MS) ~ 'same',
    # (Reference_PMID_SH==Reference_PMID_MS) & (inclusion_SH == '?' | inclusion_MS=="?") ~ 'full_text_check',
    (Reference_PMID_SH==Reference_PMID_MS) & (inclusion_SH != inclusion_MS) ~ 'discuss'
 )
) ->human_recoded2 

# select papers to discuss

# create vectors with PMIDs that need to be discussed:
human_recoded2$Reference_PMID_MS[which(human_recoded2$conclusion=='discuss')]->pmid.h
animal_recoded2$Reference_PMID_MS[which(animal_recoded2$conclusion=='discuss')]->pmid.a

# select original entries for these PMIDs
human_recoded2 %>% filter(Reference_PMID_MS %in% pmid.h) %>% write.csv2(.,file='processed_data/inconsistencies_human_s2.csv')
animal_recoded2 %>% filter(Reference_PMID_MS %in% pmid.a) %>% write.csv2(.,file='processed_data/inconsistencies_animal_s2.csv')
# # upload files to OSF
#   osf_upload(osf_retrieve_node("awkn6"),'processed_data/inconsistencies_human_s2.csv')
#   osf_upload(osf_retrieve_node("awkn6"),'processed_data/inconsistencies_animal_s2.csv')

```

#### Step 2: Merge data after discussion inconsistencies
```{r eval=FALSE, include=FALSE}
#remove columns with only na's
human_discussed_s2 <- human_discussed_s2[,colSums(is.na(human_discussed_s2))<nrow(human_discussed_s2)]

# human_discussed_s2 <- human_discussed_s2[rowSums(is.na(human_discussed_s2))<nrow(human_discussed_s2),]
# animal_discussed_s2 <- animal_discussed_s2[rowSums(is.na(animal_discussed_s2))<nrow(animal_discussed_s2),]

# merge columns from discussion to original screening data
animal_discussed_s2 %>% select(Reference_PMID_SH,!grep("_SH|_MS", colnames(animal_discussed_s2)))->animal_discussed_s22
human_discussed_s2 %>% select(Reference_PMID_SH,!grep("_SH|_MS", colnames(human_discussed_s2)))->human_discussed_s22

# merge data
full_join(human_recoded2,human_discussed_s22, by="Reference_PMID_SH")->human_new
full_join(animal_recoded2,animal_discussed_s22, by="Reference_PMID_SH")->animal_new


# Create column with new decisions:

# rename "Second.screening..yes...inclusie..no..exlusie....discussieren" to more convenient colname
 colnames(human_new)[40]<-"second.screening"
 colnames(animal_new)[43]<-"second.screening"
 
# new conclusion column human
human_new %>% mutate(
  conclusion2=
    case_when(
      conclusion1 == "same"  ~ inclusion_MS,
      (conclusion1 == "discuss" & (second.screening =="yes"| second.screening =="no")) ~ as.character(second.screening),
      (conclusion1 == "discuss" & (second.screening !="yes"| second.screening !="no")) ~ as.character(Final),
     # (conclusion1 == "discuss" & !is.na(second.screening) & is.na(Final) ) ~ as.character(second.screening),
     # (conclusion1 == "discuss" & !is.na(second.screening) )  ~ as.character(Final))
      )
)->human_new2
# check, there should be no na's
is.na(human_new2$conclusion2) %>% any()

# new conclusion colum human
animal_new %>% mutate(
  conclusion2=
    case_when(
      conclusion1 == "same"  ~ inclusion_MS,
      (conclusion1 == "discuss" & (second.screening =="yes"| second.screening =="no")) ~ as.character(second.screening),
      (conclusion1 == "discuss" & (second.screening !="yes"| second.screening !="no")) ~ as.character(Final),
      # (conclusion1 == "discuss" & !is.na(second.screening) & is.na(Final) ) ~ as.character(second.screening),
      # (conclusion1 == "discuss" & !is.na(second.screening) )  ~ as.character(Final))
    )
)->animal_new2
# check, there should be no na's
is.na(animal_new2$conclusion2) %>% any()

# export new datasets
human_new2 %>% filter(conclusion2 == "?") %>% write.csv2(.,file='processed_data/required_full_checks_human_s2.csv')
animal_new2 %>% filter(conclusion2 == "?") %>% write.csv2(.,file='processed_data/required_full_checks_animal_s2.csv')

# upload files to OSF
 # osf_upload(osf_retrieve_node("awkn6"),'processed_data/required_full_checks_human_s2.csv')
 # osf_upload(osf_retrieve_node("awkn6"),'processed_data/required_full_checks_animal_s2.csv')

```

#### Step 3: add information full text screening to data
```{r eval=FALSE, include=FALSE}
# filter new columns
full_text_check_s2_animal %>% select(  Reference_PMID_SH, Full_text_MS_notes, Full_text_MS_conclusion )->full.text.checks.animal
full_text_check_s2_human %>% select(  Reference_PMID_SH, Full_text_SH_notes, Full_text_SH_conclusion )->full.text.checks.human

# merge data
 full_join(human_new2, full.text.checks.human, by="Reference_PMID_SH")->human_screening2_complete
 full_join(animal_new2, full.text.checks.animal, by="Reference_PMID_SH")->animal_screening2_complete
 
 #create variable with final conclusions
 animal_screening2_complete %>% mutate(
   conclusion3=
     case_when(
       conclusion2!= "?" ~ conclusion2,
       conclusion2 == "?"  ~ as.character(Full_text_MS_conclusion)
     )
 )->animal_new3
 
#checks
is.na(animal_new3$conclusion3) %>% any()
(animal_new3$conclusion3 =="" )  %>% any()

 human_screening2_complete %>% mutate(
   conclusion3=
     case_when(
       conclusion2!= "?" ~ conclusion2,
       conclusion2 == "?"  ~ as.character(Full_text_SH_conclusion)
     )
 )->human_new3
 
# checks
(human_new3$conclusion3 =="")%>% any()
is.na(human_new3$conclusion3) %>% any()

# Overview of inclusions:
animal_new3 %>% filter(conclusion3 == "yes") ->animal_inclusions
human_new3 %>% filter(conclusion3 == "yes") ->human_inclusions

#export data
write.csv2(animal_inclusions,file='processed_data/animal_inclusions_s2.csv')
write.csv2(human_inclusions,file='processed_data/human_inclusions_s2.csv')
# upload files to OSF
# osf_upload(osf_retrieve_node("awkn6"),'processed_data/animal_inclusions_s2.csv')
# osf_upload(osf_retrieve_node("awkn6"),'processed_data/human_inclusions_s2.csv')
```

### For flowchart

##### Total screened animal
```{r}
nrow(SH_animal.S2)
nrow(MS_animal.S2)
# should be identical 
n.s2.A == nrow(MS_animal.S2)
```

##### Total screened human
```{r}
nrow(SH_human.S2)
nrow(MS_human.S2)
# should be identical 
n.s2.H == nrow(MS_human.S2)
```

#### Full text checks animal
```{r}
full_text_check_s2_animal %>% nrow()
```

#### Full text checks human
```{r}
full_text_check_s2_human %>% nrow()
```
 

#### Post-screeing Inclusions animal
```{r}
animal_included_s2 %>% nrow() ->s2.A.n.post.screening
s2.A.n.post.screening
```

#### Post-screeing Inclusions Human
```{r}
human_included_s2 %>% nrow() ->s2.H.n.post.screening
s2.H.n.post.screening
```


#### Inclusions after data-extraction Animal
```{r}
data.s2.animal %>% 
  filter(inclusion.final == 1) %>% 
    select(`subject`,Reference_PMID_MS ) %>% 
  distinct(Reference_PMID_MS ) %>% tally() -> s2.A.n.in.data
s2.A.n.in.data
```


#### Inclusions after data-extraction Human
```{r}
data.s2.human %>% 
  filter(inclusion.final == 1) %>% 
    select(`subject`,Reference_PMID_MS ) %>% 
  distinct(Reference_PMID_MS ) %>% tally() -> s2.H.n.in.data
s2.H.n.in.data
```

Export inclusions S2 for QA
```{r eval=FALSE, include=FALSE}
data.s2.human %>% filter(inclusion.final == 1) %>% distinct(Reference_PMID_MS ) %>% write.csv2(.,"processed_data/Human.PMIDs.QA.S2.csv")
data.s2.animal %>% filter(inclusion.final == 1) %>% distinct(Reference_PMID_MS) %>% write.csv2(.,"processed_data/Animal.PMIDs.QA.S2.csv")
```


## S3 screening

### Total screened Animal
```{r}
nrow(s3.animal) #254
# s3.animal %>% filter(inclusion.screening != "0") %>% write.csv2(.,file='processed_data/animal.inclusions.s3.csv')
# osf_upload(osf_retrieve_node("e9wmt"),'processed_data/animal.inclusions.s3.csv')
n.s3.A == nrow(s3.animal) # should be equal
```


### Total screened Human
```{r}
nrow(s3.human) # 681
# s3.human %>% filter(inclusion.screening != "0") %>% write.csv2(.,file='processed_data/human.inclusions.s3.csv')
# osf_upload(osf_retrieve_node("e9wmt"),'processed_data/human.inclusions.s3.csv')
n.s3.H == nrow(s3.human)  #should be equal
```


### Full text checks in screening (animal)
```{r}
s3.animal %>% filter(full.text.checked == 1) %>% nrow()
```


### Full text checks in screening (human)
```{r}
s3.human %>% filter(full.text.checked == 1) %>% nrow()
```


### Inclusions after screening (animal)
```{r}
s3.animal %>% filter(inclusion.screening == "?" )%>% nrow()
```

```{r}
s3.animal %>% 
   # filter(inclusion.screening == 1 ) %>%
  filter(inclusion.screening != 0 ) %>%
nrow() -> s3.A.n.post.screening # NOTE: these include 1 (=inclusion) and ?
s3.A.n.post.screening
```


### Inclusions after screening (human)
```{r}
s3.human %>%filter(inclusion.screening == "?" ) %>% nrow()
```

```{r}
s3.human %>% 
  # filter(inclusion.screening == 1 ) %>% 
    filter(inclusion.screening != 0 ) %>%
  nrow() -> s3.H.n.post.screening # NOTE: these include 1 (=inclusion) and ?
s3.H.n.post.screening
```


### Inclusions after data-extraction Animal
```{r}
data.s3.animal %>% 
  filter(inclusion.final == 1) %>% 
    select(`subject`,PMID ) %>% 
  distinct(PMID) %>% tally() -> s3.A.n.in.data
s3.A.n.in.data

s3.A.n.in.data == 68+18
```


### Inclusions after data-extraction human
```{r}
data.s3.human %>% 
  filter(inclusion.final == 1) %>% 
    select(`subject`,PMID ) %>% 
  distinct(PMID) %>% tally() -> s3.H.n.in.data  #indeed same numbers as with files above
s3.H.n.in.data
```

Export inclusions S3 for QA
```{r eval=FALSE, include=FALSE}
data.s3.human %>% filter(inclusion.final == 1) %>% distinct(PMID) %>% write.csv2(.,"processed_data/Human.PMIDs.QA.S3.csv")
data.s3.animal %>% filter(inclusion.final == 1) %>% distinct(PMID) %>% write.csv2(.,"processed_data/Animal.PMIDs.QA.S3.csv")
```


# Total screened in S1,S2,S3

## Clinical
```{r}
n.s1.H #292
n.s2.H # 142
n.s3.H # 681

n.s1.H+n.s2.H+n.s3.H == total.screened.clinical
```

## preclinical 
```{r}
n.s1.A#178
n.s2.A# 114
n.s3.A#254

n.s1.A+n.s2.A+n.s3.A == total.screened.preclinical
```

# total included in dataset
(subject 1 = human, subject 2 = preclinical)
clinical
```{r}
s1.n.in.data %>% filter(subject == 1) %>% select(n) + s2.H.n.in.data + s3.H.n.in.data
```
preclinical
```{r}
s1.n.in.data %>% filter(subject == 2) %>% select(n) + s2.A.n.in.data + s3.A.n.in.data
```

Confirm that numbers above are same as in prepared data (correct)
```{r}
dataset.prep %>% group_by(subject.cat) %>%
  summarize(papers=length(unique(PMID)), 
            groups=length(unique(new.idPTSD)),
            comparisons=length(each)) %>% data.frame()-> combined.n.in.data
combined.n.in.data
```


# Flowchart: collect data

Create summary variables for flowchart

```{r}
length(unique_screened_articles) -> total.screened
#human
s1.n.post.screening[1,2]+s2.H.n.post.screening+s3.H.n.post.screening ->post.screening.H
#animal
s1.n.post.screening[2,2]+s2.A.n.post.screening+s3.A.n.post.screening-> post.screening.A

post.screening.H$n +post.screening.A$n ->post.screening
combined.n.in.data[1,2] ->included.A
combined.n.in.data[2,2]->included.H
included.A+included.H->included
```

# Total included in analyses

## metaregression (theory-driven analysis with metafor)

Human PTSD
```{r}
metaregression.clinical%>% 
  distinct(new.idPTSD, .keep_all = TRUE) %>%
  summarize(papers=length(unique(PMID)), 
            groups=nrow(.),
            n=(round(sum(nPTSD),0))
            ) ->mReg.clinical.ptsd
mReg.clinical.ptsd
```
Human Control
```{r}
metaregression.clinical%>% 
  distinct(new.idHC, .keep_all = TRUE) %>%
  summarize(papers=length(unique(PMID)), 
            groups=nrow(.),
            n=(round(sum(nHC),0))
            ) ->mReg.clinical.hc
mReg.clinical.hc

# metaregression.clinical %>% distinct(new.idPTSD, .keep_all = TRUE) %>% nrow() # idem
```

Animal PTSD
```{r}
metaregression.preclinical %>%
  distinct(new.idPTSD, .keep_all = TRUE) %>%
  summarize(papers=length(unique(PMID)), 
            groups=nrow(.),
            n=(round(sum(nPTSD),0))
            ) ->mReg.preclinical.ptsd
mReg.preclinical.ptsd
```

Animal Control
```{r}
metaregression.preclinical %>%
  distinct(new.idHC, .keep_all = TRUE) %>%
  summarize(papers=length(unique(PMID)), 
            groups=nrow(.),
            n=(round(sum(nHC),0))
            ) ->mReg.preclinical.hc
mReg.preclinical.hc
```

## Metaforest (data-driven analysis)

Human
```{r}
explorative.clinical %>%
  summarize(groups=length(unique(new.idPTSD))) %>% data.frame()->metaforest.clinical
metaforest.clinical
```
Animal
```{r}
explorative.preclinical %>%
  summarize(groups=length(unique(new.idPTSD))) %>% data.frame()->metaforest.preclinical
metaforest.preclinical$groups
```

## Count metareg used in flowchart (metareg + metaforst identical n)
```{r}
# same number of independent ptsd groups included in metaregression, metaforest/metacart?
metaforest.preclinical$groups == mReg.preclinical.ptsd$groups# yes
metaforest.clinical$groups == mReg.clinical.ptsd$groups # yes
# -> count metareg used in flowchart
```


# Flowchart: Figure

https://www.r-bloggers.com/2018/05/flow-charts-in-r/
```{r}
tiff(file="results/flowchart.tiff", height = 2200, width = 2600, res=300)

grid.newpage()
# set some parameters to use repeatedly
leftx <- .35
midx <- .5
rightx <- .65
width <- .175
gp <- gpar(fill = "lightgrey")

# create boxes
(total <- boxGrob(paste0("Screened Records\n N =",total.screened,"*\n*",length(screened_articles) - length(unique_screened_articles)," with clinical and preclinical data"), 
 x=midx, y=0.9, box_gp = gp, width = width+.15))

(g1 <- boxGrob(paste0("Screened clinical\n studies N = ",total.screened.clinical), 
 x=leftx, y=.7, box_gp = gp, width = width))
(g2 <- boxGrob(paste0("Screened preclinical\n studies N = ",total.screened.preclinical), 
 x=rightx, y=.7, box_gp = gp, width = width))

connectGrob(total, g1, "N")
connectGrob(total, g2, "N")

(inel.cl1 <- boxGrob(paste0("Title & Abstract\nExclusions\nN = ",total.screened.clinical-post.screening.H$n),
 x=.125, y=.625, box_gp = gp, width = .14, height = .10))

(inel.precl1 <- boxGrob(paste0("Title & Abstract\nExclusions\nN = ",total.screened.preclinical-post.screening.A$n),
 x=.875, y=.625, box_gp = gp, width = .14, height = .10))

connectGrob(g1, inel.cl1, "-")
connectGrob(g2, inel.precl1, "-")

(g11 <- boxGrob(paste0("Eligible clinical\n studies N = ",post.screening.H$n),
 x=leftx, y=.525, box_gp = gp, width = width))
(g21 <- boxGrob(paste0("Eligible preclinical\n studies N = ",post.screening.A$n),
 x=rightx, y=.525, box_gp = gp, width = width))
 
connectGrob(g1, g11, "N")
connectGrob(g2, g21, "N")

(inel.cl2 <- boxGrob(paste0("Full-text\nExclusions\nN = ",post.screening.H$n-combined.n.in.data[2,2]),
 x=.125, y=.45, box_gp = gp, width = .14, height = .10))

(inel.precl2 <- boxGrob(paste0("Full-text\nExclusions\nN = ",post.screening.A$n-combined.n.in.data[1,2]),
 x=.875, y=.45, box_gp = gp, width = .14, height = .10))

connectGrob(g11, inel.cl2, "-")
connectGrob(g21, inel.precl2, "-")

(g12 <- boxGrob(paste0("Included clinical\n studies N=", combined.n.in.data[2,2]), 
 x=leftx, y=.35, box_gp = gp, width = width))
(g22 <- boxGrob(paste0("Included preclinical\n studies N=", combined.n.in.data[1,2]), 
 x=rightx, y=.35, box_gp = gp, width = width))

connectGrob(g11, g12, "N")
connectGrob(g21, g22, "N")

# comparison b excluded for meta-analysis -> no papers excluded but 2 comparison groups
# (inel.cl3 <- boxGrob(paste0("comparison B excluded \n N = ",combined.n.in.data[2,2]-mReg.clinical.ptsd$papers),
 # x=.1, y=.25, box_gp = gp, width = .125, height = .06))

# connectGrob(g12, inel.cl3, "-")

(g13 <- boxGrob(paste0(
   "In meta-analysis of clinical studies:\n- ",
 mReg.clinical.ptsd$n, " unique PTSD patients in \n", mReg.clinical.ptsd$groups, " independent groups\n - ",
 mReg.clinical.hc$n, " unique healthy controls in \n",  mReg.clinical.hc$groups, " independent groups" ),
 x=leftx-0.1, y=.125, box_gp = gp, width = width+0.2))

  (g23 <- boxGrob(paste0(
 "In meta-analysis of preclinical studies:\n- ",
 mReg.preclinical.ptsd$n, " unique 'PTSD-like' animals in \n", mReg.preclinical.ptsd$groups, " independent groups\n - ",
 mReg.preclinical.hc$n, " unique control animals in \n",  mReg.preclinical.hc$groups, " independent groups"),
  
 x=rightx+0.1, y=.125, box_gp = gp, width = width+0.2))

connectGrob(g12, g13, "v")
connectGrob(g22, g23, "v")

dev.off()
```

total number of humans
```{r}
2611+4121 #6732
mReg.clinical.ptsd$n + mReg.clinical.hc$n 
```

total number of animals
```{r}
3407+3427 #6834
mReg.preclinical.ptsd$n + mReg.preclinical.hc$n
```
