---
title: "Merge_datasets"
author: "Milou Sep"
date: "4/6/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
rm(list = ls()) #clean environment
# load files from OSF
library(osfr)
# Authenticate to OSF (see: http://centerforopenscience.github.io/osfr/articles/auth.html). Via osf_auth("PAT") in the commentline. (note PAT can be derived from OSF)

library(readxl)
library(dplyr)
```

# retrieve OSF files 
```{r}
osf_retrieve_file("tqmwb") %>% osf_download(path = "data", conflicts="overwrite") # search 1
osf_retrieve_file("xqpm3") %>% osf_download(path = "data", conflicts="overwrite") # search 2
osf_retrieve_file("wbrcm") %>% osf_download(path = "data", conflicts="overwrite") # search 3
```

# load data
```{r}
s1 <- read_excel("data/TRACE data_collection_search1.xlsx", na = c(" ", "-", "not reported"), col_types = "text")#s1
s2a <- read_excel("data/TRACE data_collection_search2.xlsx", sheet = "animal_inclusions_s2", na = c(" ", "-", "not reported"), col_types = "text")#s2
s2h <- read_excel("data/TRACE data_collection_search2.xlsx", sheet = "human_inclusions_s2", na = c(" ", "-", "not reported"), col_types = "text")#s2
s3a <- read_excel("data/TRACE_data_collection_search3.xlsx", sheet = "animal.inclusions.s3", na = c(" ", "-", "not reported"), col_types = "text")#s3
s3h <- read_excel("data/TRACE_data_collection_search3.xlsx", sheet = "human.inclusions.s3", na = c(" ", "-", "not reported"), col_types = "text")#s3
```

# select and rename S1
```{r}
str(s1)

df1 <- select(s1,  `Reference_First Author` , `Reference_Publication Year` , `Reference_PMID` , `inclusion` , `subject` ,  `Data_Subjects_n_ptsd` , `Data_Subjects_n_control` , `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , `Data_Subjects_gender_control (M = male; F = female; - = not reported)`,
              PTSD.age.recoded, HC.age.recoded,
              
              #, `Data_Subjects_m_Age_ptsd (- = not reported)` , `Data_Subjects_sd_Age_ptsd (- = not reported)` , `Data_Subjects_m_Age_control (- = not reported)` , `Data_Subjects_sd_Age_control (- = not reported)` , 
              
              
              `Data_Subjects_FS_#Shocks` , `Data_Subjects_FS_Amperage(mA)` , `Data_Subjects_PTSDtypeSHORT2` , `Data_Subjects_Controltype` , `Data_Subjects_Strain_or_Population` , `Data_Subjects_ptsd-measure` , `Data_Method_TimeTask-Trauma` , `task` , 
              
              # `Data_Method_animal light dark testing?` , 
              rhythm_recoded,
              
              `measure` , `Comparison` , `ID_Experimental_group` , `ID_Control_group` , `Data_Outcome1_VarName` , `Data_Outcome1_M` , `Data_Outcome1_SD` , `Data_Outcome1_SEM` , `Data_Outcome2_VarName` , `Data_Outcome2_M` , `Data_Outcome2_SD` , `Data_Outcome2_SEM` )

# Rename
df1 %>% rename(
  author =  `Reference_First Author` , 
  year = `Reference_Publication Year` , 
  PMID = `Reference_PMID` , 
  decision = `inclusion` , 
  subject = `subject` , 
  nPTSD = `Data_Subjects_n_ptsd` , 
  nHC =`Data_Subjects_n_control` , 
  sex.PTSD = `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , 
  sex.HC =`Data_Subjects_gender_control (M = male; F = female; - = not reported)` ,
  # age.PTSD.m =`Data_Subjects_m_Age_ptsd (- = not reported)` , 
  # age.PTSD.sd =`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
  # age.HC.m =`Data_Subjects_m_Age_control (- = not reported)` ,
  # age.HC.sd =`Data_Subjects_sd_Age_control (- = not reported)` ,
  
  age.PTSD = PTSD.age.recoded,
  age.HC = HC.age.recoded,
  
  shocks.num = `Data_Subjects_FS_#Shocks` , 
  shocks.amp =`Data_Subjects_FS_Amperage(mA)` , 
  ptsd.type = `Data_Subjects_PTSDtypeSHORT2` , 
  control.type = `Data_Subjects_Controltype` , 
  population = `Data_Subjects_Strain_or_Population` , 
  ptsd.measure = `Data_Subjects_ptsd-measure` , 
  time = `Data_Method_TimeTask-Trauma` , 
  task = `task` , 
  
  # rhythm  =`Data_Method_animal light dark testing?` , 
  rhythm  = rhythm_recoded,
  
  measure = `measure` , 
  comparison = `Comparison` , 
  idPTSD =`ID_Experimental_group` , 
  idHC = `ID_Control_group` , 
  outcomePTSD = `Data_Outcome1_VarName` , 
  meanPTSD = `Data_Outcome1_M` , 
  sdPTSD = `Data_Outcome1_SD` , 
  semPTSD = `Data_Outcome1_SEM` , 
  outcomeHC = `Data_Outcome2_VarName` , 
  meanHC =`Data_Outcome2_M` , 
  sdHC = `Data_Outcome2_SD` , 
  semHC = `Data_Outcome2_SEM` 
) -> df1.renamed

glimpse(df1.renamed)

# add missing colums
df1.renamed$res.sus.split <-"NA"
```

# select and rename S2

## s2 animal
```{r}
str(s2a)

df2a <- select(s2a,
               `Reference_First Author_SH` , `Reference_Publication Year_SH` , `Reference_PMID_SH` , `inclusion.final` , `subject` , `Data_Subjects_n_ptsd` , `Data_Subjects_n_control` , `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , `Data_Subjects_gender_control (M = male; F = female; - = not reported)` , 
               
               PTSD.age.recoded, HC.age.recoded,
               
               #`Data_Subjects_m_Age_ptsd (- = not reported)` , `Data_Subjects_sd_Age_ptsd (- = not reported)` , `Data_Subjects_m_Age_control (- = not reported)` , `Data_Subjects_sd_Age_control (- = not reported)` , 
               
               `Data_Subjects_FS_#Shocks` , `Data_Subjects_FS_Amperage(mA)` , `Data_Subjects_PTSDtypeSHORT2` , `Data_Subjects_Controltype` , `Data_Subjects_Strain_or_Population` , `Data_Subjects_ptsd-measure` , `Data_Subjects_ResSus.split` , `Data_Method_TimeTask-Trauma` , `task` , 
               
               #`Data_Method_animal light dark testing?` , 
               
               rhythm_recoded,
               
               `measure` , `Comparison` , `ID_Experimental_group` , `ID_Control_group` , `Data_Outcome1_VarName` , `Data_Outcome1_M` , `Data_Outcome1_SD` , `Data_Outcome1_SEM` , `Data_Outcome2_VarName` , `Data_Outcome2_M` , `Data_Outcome2_SD` , `Data_Outcome2_SEM` )


df2a %>% rename(
  author =  `Reference_First Author_SH` , 
  year = `Reference_Publication Year_SH` , 
  PMID = `Reference_PMID_SH` , 
  decision = `inclusion.final` , 
  subject = `subject` , 
  nPTSD = `Data_Subjects_n_ptsd` , 
  nHC =`Data_Subjects_n_control` , 
  sex.PTSD = `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , 
  sex.HC =`Data_Subjects_gender_control (M = male; F = female; - = not reported)` ,
  
  # age.PTSD.m =`Data_Subjects_m_Age_ptsd (- = not reported)` , 
  # age.PTSD.sd =`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
  # age.HC.m =`Data_Subjects_m_Age_control (- = not reported)` ,
  # age.HC.sd =`Data_Subjects_sd_Age_control (- = not reported)` ,
  
  age.PTSD = PTSD.age.recoded,
  age.HC = HC.age.recoded,
  
  shocks.num = `Data_Subjects_FS_#Shocks` , 
  shocks.amp =`Data_Subjects_FS_Amperage(mA)` , 
  ptsd.type = `Data_Subjects_PTSDtypeSHORT2` , 
  control.type = `Data_Subjects_Controltype` , 
  population = `Data_Subjects_Strain_or_Population` , 
  ptsd.measure = `Data_Subjects_ptsd-measure` , 
  
  # not in s1 or human
  res.sus.split = `Data_Subjects_ResSus.split`,
  
  time = `Data_Method_TimeTask-Trauma` , 
  task = `task` , 
  # rhythm  =`Data_Method_animal light dark testing?` , 
  
  rhythm = rhythm_recoded,
  
  measure = `measure` , 
  comparison = `Comparison` , 
  idPTSD =`ID_Experimental_group` , 
  idHC = `ID_Control_group` , 
  outcomePTSD = `Data_Outcome1_VarName` , 
  meanPTSD = `Data_Outcome1_M` , 
  sdPTSD = `Data_Outcome1_SD` , 
  semPTSD = `Data_Outcome1_SEM` , 
  outcomeHC = `Data_Outcome2_VarName` , 
  meanHC =`Data_Outcome2_M` , 
  sdHC = `Data_Outcome2_SD` , 
  semHC = `Data_Outcome2_SEM` 
) -> df2a.renamed

glimpse(df2a.renamed)


```

## s2 human
```{r}
str(s2h)

df2h <- select(s2h,
               `Reference_First Author_SH` , `Reference_Publication Year_SH` , `Reference_PMID_SH` , `inclusion.final` , `subject` , `Data_Subjects_n_ptsd` , `Data_Subjects_n_control` , `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , `Data_Subjects_gender_control (M = male; F = female; - = not reported)` , 
               
               `Data_Subjects_m_Age_ptsd (- = not reported)` , #`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
               `Data_Subjects_m_Age_control (- = not reported)` , #`Data_Subjects_sd_Age_control (- = not reported)` , 
               
               `Data_Subjects_FS_#Shocks` , `Data_Subjects_FS_Amperage(mA)` , `Data_Subjects_PTSDtypeSHORT2` , `Data_Subjects_Controltype` , `Data_Subjects_Strain_or_Population` , `Data_Subjects_ptsd-measure` , #`Data_Subjects_ResSus.split` , 
               `Data_Method_TimeTask-Trauma` , `task` , 
               
               #`Data_Method_animal light dark testing?` , 
               
               `measure` , `Comparison` , `ID_Experimental_group` , `ID_Control_group` , `Data_Outcome1_VarName` , `Data_Outcome1_M` , `Data_Outcome1_SD` , `Data_Outcome1_SEM` , `Data_Outcome2_VarName` , `Data_Outcome2_M` , `Data_Outcome2_SD` , `Data_Outcome2_SEM` )


df2h %>% rename(
  author =  `Reference_First Author_SH` , 
  year = `Reference_Publication Year_SH` , 
  PMID = `Reference_PMID_SH` , 
  decision = `inclusion.final` , 
  subject = `subject` , 
  nPTSD = `Data_Subjects_n_ptsd` , 
  nHC =`Data_Subjects_n_control` , 
  sex.PTSD = `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , 
  sex.HC =`Data_Subjects_gender_control (M = male; F = female; - = not reported)` ,
  
  # age.PTSD.m =`Data_Subjects_m_Age_ptsd (- = not reported)` , 
  # age.PTSD.sd =`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
  # age.HC.m =`Data_Subjects_m_Age_control (- = not reported)` ,
  # age.HC.sd =`Data_Subjects_sd_Age_control (- = not reported)` ,
  
  age.PTSD = `Data_Subjects_m_Age_ptsd (- = not reported)`,
  age.HC = `Data_Subjects_m_Age_control (- = not reported)`,
  
  shocks.num = `Data_Subjects_FS_#Shocks` , 
  shocks.amp =`Data_Subjects_FS_Amperage(mA)` , 
  ptsd.type = `Data_Subjects_PTSDtypeSHORT2` , 
  control.type = `Data_Subjects_Controltype` , 
  population = `Data_Subjects_Strain_or_Population` , 
  ptsd.measure = `Data_Subjects_ptsd-measure` , 
  
  # not in s1 or human
  # res.sus.split = `Data_Subjects_ResSus.split`,
  
  time = `Data_Method_TimeTask-Trauma` , 
  task = `task` , 
  
  # rhythm  =`Data_Method_animal light dark testing?` , 
  
  measure = `measure` , 
  comparison = `Comparison` , 
  idPTSD =`ID_Experimental_group` , 
  idHC = `ID_Control_group` , 
  outcomePTSD = `Data_Outcome1_VarName` , 
  meanPTSD = `Data_Outcome1_M` , 
  sdPTSD = `Data_Outcome1_SD` , 
  semPTSD = `Data_Outcome1_SEM` , 
  outcomeHC = `Data_Outcome2_VarName` , 
  meanHC =`Data_Outcome2_M` , 
  sdHC = `Data_Outcome2_SD` , 
  semHC = `Data_Outcome2_SEM` 
) -> df2h.renamed

glimpse(df2h.renamed)

# add missing columns
df2h.renamed$res.sus.split <-"NA"
df2h.renamed$rhythm <- "NA"
```


# select and rename S3

## S3 animal
```{r}
str(s3a)

df3a <- select(s3a,
               `First Author` , `Publication Year` , `PMID` , `inclusion.final` , `subject` , `Data_Subjects_n_ptsd` , `Data_Subjects_n_control` , `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , `Data_Subjects_gender_control (M = male; F = female; - = not reported)` , 
               
               PTSD.age.recoded, HC.age.recoded,
               
               #`Data_Subjects_m_Age_ptsd (- = not reported)` , `Data_Subjects_sd_Age_ptsd (- = not reported)` , `Data_Subjects_m_Age_control (- = not reported)` , `Data_Subjects_sd_Age_control (- = not reported)` ,
               
               `Data_Subjects_FS_#Shocks` , `Data_Subjects_FS_Amperage(mA)` , `Data_Subjects_PTSDtypeSHORT2` , `Data_Subjects_Controltype` , `Data_Subjects_Strain_or_Population` ,
               #`Data_Subjects_ptsd-measure` , 
               
               `Data_Subjects_ResSus.split.final` , 
               
               `Data_Method_TimeTask-Trauma` , `task` , 
               
               # `Data_Method_animal light dark testing?` , 
               rhythm_recoded,
               
               
               `measure` , `Comparison` , `ID_Experimental_group` , `ID_Control_group` , `Data_Outcome1_VarName` , `Data_Outcome1_M` , `Data_Outcome1_SD` , `Data_Outcome1_SEM` , `Data_Outcome2_VarName` , `Data_Outcome2_M` , `Data_Outcome2_SD` , `Data_Outcome2_SEM` )



df3a %>% rename(
  author =  `First Author` , 
  year = `Publication Year` , 
  PMID = `PMID` , 
  decision = `inclusion.final` , 
  subject = `subject` , 
  nPTSD = `Data_Subjects_n_ptsd` , 
  nHC =`Data_Subjects_n_control` , 
  sex.PTSD = `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , 
  sex.HC =`Data_Subjects_gender_control (M = male; F = female; - = not reported)` ,
  # age.PTSD.m =`Data_Subjects_m_Age_ptsd (- = not reported)` , 
  # age.PTSD.sd =`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
  # age.HC.m =`Data_Subjects_m_Age_control (- = not reported)` ,
  # age.HC.sd =`Data_Subjects_sd_Age_control (- = not reported)` ,
  
  age.PTSD = PTSD.age.recoded,
  age.HC = HC.age.recoded,
  
  shocks.num = `Data_Subjects_FS_#Shocks` , 
  shocks.amp =`Data_Subjects_FS_Amperage(mA)` , 
  ptsd.type = `Data_Subjects_PTSDtypeSHORT2` , 
  control.type = `Data_Subjects_Controltype` , 
  population = `Data_Subjects_Strain_or_Population` , 
  
  # only in human s3
  # ptsd.measure = `Data_Subjects_ptsd-measure` , 
  
  # not in s1 or human s2
  res.sus.split = `Data_Subjects_ResSus.split.final`,
  
  time = `Data_Method_TimeTask-Trauma` , 
  task = `task` , 
  
  # rhythm  =`Data_Method_animal light dark testing?` , 
  rhythm = rhythm_recoded,
  
  measure = `measure` , 
  comparison = `Comparison` , 
  idPTSD =`ID_Experimental_group` , 
  idHC = `ID_Control_group` , 
  outcomePTSD = `Data_Outcome1_VarName` , 
  meanPTSD = `Data_Outcome1_M` , 
  sdPTSD = `Data_Outcome1_SD` , 
  semPTSD = `Data_Outcome1_SEM` , 
  outcomeHC = `Data_Outcome2_VarName` , 
  meanHC =`Data_Outcome2_M` , 
  sdHC = `Data_Outcome2_SD` , 
  semHC = `Data_Outcome2_SEM` 
) -> df3a.renamed

# add missing columns
df3a.renamed$ptsd.measure <-"NA"
```

## S3 human

```{r}

str(s3h)

df3h <- select(s3h,
               `First Author` , `Publication Year` , `PMID` , `inclusion.final` , `subject` , `Data_Subjects_n_ptsd` , `Data_Subjects_n_control` , `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , `Data_Subjects_gender_control (M = male; F = female; - = not reported)` , 
               
               `Data_Subjects_m_Age_ptsd (- = not reported)` , #`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
               `Data_Subjects_m_Age_control (- = not reported)` , #`Data_Subjects_sd_Age_control (- = not reported)` ,
               
               #`Data_Subjects_FS_#Shocks` , `Data_Subjects_FS_Amperage(mA)` , 
               
               `Data_Subjects_PTSDtypeSHORT2` , `Data_Subjects_Controltype` , `Data_Subjects_Strain_or_Population` , `Data_Subjects_ptsd-measure` , 
               
               #`Data_Subjects_ResSus.split.final` , 
               
               `Data_Method_TimeTask-Trauma` , `task` , 
               
               # `Data_Method_animal light dark testing?` , 
               
               `measure` , `Comparison` , `ID_Experimental_group` , `ID_Control_group` , `Data_Outcome1_VarName` , `Data_Outcome1_M` , `Data_Outcome1_SD` , `Data_Outcome1_SEM` , `Data_Outcome2_VarName` , `Data_Outcome2_M` , `Data_Outcome2_SD` , `Data_Outcome2_SEM` ) 


df3h %>% rename(
  author =  `First Author` , 
  year = `Publication Year` , 
  PMID = `PMID` , 
  decision = `inclusion.final` , 
  subject = `subject` , 
  nPTSD = `Data_Subjects_n_ptsd` , 
  nHC =`Data_Subjects_n_control` , 
  sex.PTSD = `Data_Subjects_gender_ptsd (M = male; F = female; - = not reported)` , 
  sex.HC =`Data_Subjects_gender_control (M = male; F = female; - = not reported)` ,
  # age.PTSD.m =`Data_Subjects_m_Age_ptsd (- = not reported)` , 
  # age.PTSD.sd =`Data_Subjects_sd_Age_ptsd (- = not reported)` , 
  # age.HC.m =`Data_Subjects_m_Age_control (- = not reported)` ,
  # age.HC.sd =`Data_Subjects_sd_Age_control (- = not reported)` ,
  
  age.PTSD = `Data_Subjects_m_Age_ptsd (- = not reported)`,
  age.HC = `Data_Subjects_m_Age_control (- = not reported)`,
  
  # only in animal s3
  # shocks.num = `Data_Subjects_FS_#Shocks` , 
  # shocks.amp =`Data_Subjects_FS_Amperage(mA)` , 
  
  ptsd.type = `Data_Subjects_PTSDtypeSHORT2` , 
  control.type = `Data_Subjects_Controltype` , 
  population = `Data_Subjects_Strain_or_Population` , 
  
  # only in human s3
  ptsd.measure = `Data_Subjects_ptsd-measure` , 
  
  # not in s1 or human s2
  # res.sus.split = `Data_Subjects_ResSus.split.final`,
  
  time = `Data_Method_TimeTask-Trauma` , 
  task = `task` , 
  
  measure = `measure` , 
  comparison = `Comparison` , 
  idPTSD =`ID_Experimental_group` , 
  idHC = `ID_Control_group` , 
  outcomePTSD = `Data_Outcome1_VarName` , 
  meanPTSD = `Data_Outcome1_M` , 
  sdPTSD = `Data_Outcome1_SD` , 
  semPTSD = `Data_Outcome1_SEM` , 
  outcomeHC = `Data_Outcome2_VarName` , 
  meanHC =`Data_Outcome2_M` , 
  sdHC = `Data_Outcome2_SD` , 
  semHC = `Data_Outcome2_SEM` 
) -> df3h.renamed


# add missing columns
df3h.renamed$shocks.num<-"NA"
df3h.renamed$shocks.amp<-"NA"
df3h.renamed$res.sus.split<-"NA"
df3h.renamed$rhythm<-"NA"

glimpse(df3h.renamed)
```


```{r eval=FALSE, include=FALSE}
df1.renamed$author # all ok
df2a.renamed$author #(incl voorletter)
df2h.renamed$author # all ok
df3a.renamed$author #(incl voorletter).. en gekke typo in naam
df3h.renamed$author # meerdere gekke typos in name P‚àö‚àÇhlchen D

```

# remove unneeded dataframes
```{r}
rm(s1, s2a, s2h, s3a, s3h,
   df1, df2a, df2h, df3a, df3h)
```

# check if data has same columns
```{r}
all_equal(df1.renamed, df2a.renamed, ignore_col_order=T)
all_equal(df2a.renamed, df2h.renamed, ignore_col_order=T)
all_equal(df1.renamed, df3a.renamed, ignore_col_order=T)
all_equal(df3a.renamed, df3h.renamed, ignore_col_order=T)
```


# merge data
```{r}
full_join(df1.renamed, df2a.renamed) %>%
  full_join(., df2h.renamed) %>%
  full_join(., df3a.renamed) %>%
  full_join(., df3h.renamed) -> merged.data
glimpse(merged.data)
```



# Recode age: set age groups

subject:
(0=humanmixed(Civiel&Military); 1=ActiveDutyMilitary; 2=Veteran; 12=ActiveDutyMilitary & Veteran; 3=Civilian; 4=Rat; 5=Mice)

refs for age groups
- [https://www.jax.org/news-and-insights/jax-blog/2017/november/when-are-mice-considered-old#]
- [https://www.jax.org/news-and-insights/jax-blog/2017/november/when-are-mice-considered-old#] (based on C557BL/6J)
- [https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3733029/[ table 2]

- week month calculations
https://www.google.com/search?q=2+months+weeks&oq=2+months+weeks&aqs=chrome..69i57j0i22i30l3.1762j0j4&sourceid=chrome&ie=UTF-8

```{r}
merged.data %>% mutate(
  
  # ptsd age
  age.PTSD2 = as.numeric(age.PTSD),
  age.PTSD.cat = case_when(
    age.PTSD == 'adult'~'(mature) adult',
    #human
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 < 20) ~ "young adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 >= 20 & age.PTSD2 <35) ~ "(mature) adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 >=35  & age.PTSD2 <50) ~ "middle-aged",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 >=50) ~ "old adult",
    # rat
    (subject == "4") & (age.PTSD2 < 26) ~ "young adult", # < 6months ~ 26.0715 weeks
    (subject == "4") & (age.PTSD2 >= 26 & age.PTSD2 <52) ~ "(mature) adult", # 6 months - 12 months (= 52)
    (subject == "4") & (age.PTSD2 >= 52 & age.PTSD2 <78) ~ "middle-aged", # 12 months - 18 months (= 78)
    (subject == "4") & (age.PTSD2 >=78) ~ "old adult",
    # mice
    (subject == "5") & (age.PTSD2 < 13) ~ "young adult", # 3 months
    (subject == "5") & (age.PTSD2 >= 13 & age.PTSD2 <26) ~ "(mature) adult", # 3-6 months
    (subject == "5") & (age.PTSD2 >= 26 & age.PTSD2 <60) ~ "middle-aged", # 10 - 14 months -> 6 - 14 (60 weeks)
    (subject == "5") & (age.PTSD2 >=60) ~ "old adult" 
  ),
  
  # HC
  age.HC2 = as.numeric(age.HC),
  age.HC.cat = case_when(
    age.HC == 'adult'~'(mature) adult',
    #human
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 < 20) ~ "young adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 >= 20 & age.HC2 <35) ~ "(mature) adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 >=35  & age.HC2 <50) ~ "middle-aged",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 >=50) ~ "old adult",
    
    # rat
    (subject == "4") & (age.HC2 < 26) ~ "young adult", # < 6months ~ 26.0715 weeks
    (subject == "4") & (age.HC2 >= 26 & age.HC2 <52) ~ "(mature) adult", # 6 months - 12 months (= 52)
    (subject == "4") & (age.HC2 >= 52 & age.HC2 <78) ~ "middle-aged", # 12 months - 18 months (= 78)
    (subject == "4") & (age.HC2 >=78) ~ "old adult",
    
    # mice
    (subject == "5") & (age.HC2 < 13) ~ "young adult", # 3 months
    (subject == "5") & (age.HC2 >= 13 & age.HC2 <26) ~ "(mature) adult", # 3-6 months
    (subject == "5") & (age.HC2 >= 26 & age.HC2 <60) ~ "middle-aged", # 10 - 14 months -> 6 - 14 (60 weeks)
    (subject == "5") & (age.HC2 >=60) ~ "old adult" 
  )
  
)-> merged.data.recoded
```


```{r eval=FALSE, include=FALSE}
# for checking
merged.data.recoded %>% select(subject, decision, age.PTSD, age.PTSD2, age.PTSD.cat,
                               age.HC, age.HC2, age.HC.cat) %>% View()
```

no missing values after recoding age in included papers
```{r eval=FALSE, include=FALSE}
merged.data.recoded %>% select(subject, decision, age.PTSD, age.PTSD2, age.PTSD.cat,
                               age.HC, age.HC2, age.HC.cat) %>% filter(decision ==1) %>% filter(is.na(.))
```


```{r eval=FALSE, include=FALSE}
merged.data.recoded %>% filter(age.PTSD2 > 65) %>% filter(decision ==1) %>% View()
merged.data.recoded %>% filter(age.HC2 > 65) %>% filter(decision ==1) %>% View()
```

```{r}
merged.data.recoded %>% select(!c(age.PTSD, age.PTSD2, age.HC, age.HC2))-> merged.data.recoded2
```


# recode rhytem

```{r}

merged.data.recoded2 %>% 
  mutate(rhythm = ifelse(subject %in% c("0", "1", "2", "12", "3"),"active", rhythm)) -> merged.data.recoded3
 
merged.data.recoded3$rhythm <- recode(merged.data.recoded3$rhythm, 'dark' = 'active', 'light' = 'inactive')

# for checking
merged.data.recoded3 %>% filter(decision == 1) %>% filter(is.na(rhythm)) # good


```



# set variable types
         
all are current character
```{r variable types}
names(merged.data.recoded3) 

string_names <- c("author", "year",

"shocks.num", "shocks.amp",

"time", "rhythm",
"idPTSD", "idHC",

"outcomePTSD", "outcomeHC"
)

factor_names <-c("PMID", "decision", "subject", "sex.PTSD", "sex.HC",
"ptsd.type", 'control.type', 'population',"ptsd.measure", 

"task", "measure",
"comparison",
"res.sus.split", "age.PTSD.cat", "age.HC.cat"
)

numeric_names <- c("nPTSD", "nHC", "meanPTSD", "sdPTSD", "semPTSD", "meanHC", "sdHC", "semHC")

# For checking -> ok!
# merged.data.recoded2 %>% mutate_at(.vars=numeric_names, as.numeric) %>% filter(decision == 1) %>% select(numeric_names) %>% is.na() %>% View()



merged.data.recoded3 %>% 
mutate_at(.vars=numeric_names, as.numeric) %>% 
mutate_at(.vars=factor_names, factor) ->merged.data.recoded4

# for checking
 # cbind(merged.data.recoded3$nHC,merged.data.recoded4$nHC)
unique(merged.data.recoded4$author) %>% data.frame() %>%head()
str(merged.data.recoded4)
```



```{r save}
 saveRDS(merged.data.recoded4, "processed_data/TRACEmerged.RDS")
write.csv2(merged.data.recoded4, "processed_data/TRACEmerged.csv", fileEncoding = "UTF-8") # writes spec characters weird
# write.table(merged.data.recoded4, "processed_data/TRACEmerged2.csv")
```

