---
title: "meta-CART TRACE"
author: "Milou Sep"
date: "4/9/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Prepare environment
```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(metacart)
library(caret)
library(metaforest)
library(ggpubr)
library(grid)
library(gridExtra)
library(purrr)
library(viridis)
```

# Methods info
## metaForest: random forest (= multiple trees)
```{r}
ModelInfo_mf()$notes # method from metaforest
```
## metaCART: tree-model
- strength of the package metacart is that it can easily explore the interaction effects among multiple moderators using an interpretable tree model.
- multi-categorical variables, it creates automatically the contrasts between (combinations of) categories that account for the highest amount of heterogeneity.
REF: 1. Li X, Dusseldorp E, Su X, Meulman JJ. Multiple moderator meta-analysis using the R-package Meta-CART. Behav Res Methods [Internet]. 2020;52(6):2657–73. Available from: http://dx.doi.org/10.3758/s13428-020-01360-0
- RE model
- c=0.5
- recommended to use lookahead = T (especially in REmrt)
- maxL 10. Same as in: [1. Li X, Dusseldorp E, Su X, Meulman JJ. Multiple moderator meta-analysis using the R-package Meta-CART. Behav Res Methods. 2020;52(6):2657-2673. doi:10.3758/s13428-020-01360-0]


# Prepare data
## load and select data
```{r data}
data<-readRDS("processed_data/TRACEprepared.RData")

data %>% 
  select(subject, sex.PTSD, control.type, ptsd.type2, population2, measure2, time.pseudo, rhythm, comparison, new.idPTSD, age.PTSD.cat, subject.cat, type, phase, valence, cuectx, yi, vi) %>% 
  droplevels() %>%
  #better variable names for plots
  rename(
    sample=subject,
    sex=sex.PTSD,
    ptsd.type=ptsd.type2,
    population=population2,
    measure=measure2,
    time.since.trauma=time.pseudo,
    age=age.PTSD.cat,
    information.type=type,
    cue.context=cuectx
  ) %>%
  # set new factor levels
  mutate(
    sex=factor(sex, levels=c("F","M", "MF"), labels = c("Female", "Male", "Mixed")),
    control.type=factor(control.type, levels=c("UnExp", "ShamExp", "TraumaExp"), labels = c("Unexposed", "Sham-exposed", "Trauma-exposed")),
    phase=factor(phase, levels=c("L", "M", "E"), labels = c( "Learning", "Memory", "Extinction")),
    valence=factor(valence, levels=c("N", "E", "F", "T"), labels = c("Neutral", "Emotional", "Fear", "Trauma")),
    cue.context=factor(cue.context, levels=c("cue", "cuecue", "cuecontext", "context"), labels = c("Cue", "Cue-Cue", "Cue-Context", "Context"))
  )-> data.explore

saveRDS(data.explore, "processed_data/data.explore.rds") # save to use later in data descriptives script.
```

## fix missing values
are there missing values?
```{r}
is.na(data.explore) %>% any()
```
are there variables with > 1/3 missing?
```{r}
which(colSums(is.na(data.explore)) > (1/3)*nrow(data.explore)) # no values with 1/3 missing
```
check variable types
```{r}
str(data.explore) # all correct
```
check missing values
```{r}
summary(data.frame(data.explore)) # in sex and time.since.trauma 
```
Imputation median and most prevalent category for numeric and factor variables respectively
```{r}
factors.to.fix <- c("sex")
numeric.to.fix <- c("time.since.trauma")
for (i in c(1:length(numeric.to.fix))) {
  numeric.to.fix[[i]] -> varname
  data.explore[is.na(data.explore[,varname]),varname] <- median(unlist(data.explore[,varname]), na.rm = T)
}
#categorical missing: substitute with most common category
categorical_mode <- function(x){names(table(x))[which.max(table(x))]}
for (i in c(1:length(factors.to.fix))) {
  factors.to.fix[[i]] -> varname
  data.explore[is.na(data.explore[,varname]),varname] <- categorical_mode(unlist(data.explore[,varname]))
}
# Confirm absence of missing values
summary(data.frame(data.explore))
any(is.na(data.explore))
```


## split clinical and preclinical data 

Comparison B [B=non-exposed vs trauma exposed no PTSD (human)] is excluded from clinical data, as the experimental group does not contain PTSD patients. Note, this comparison is used in the sensitivity analysis of the theory driven analysis. The comparison variable is also excluded from the human dataset, as the difference between comparison A [A= non-exposed vs trauma-exposed PTSD (human)] and comparison C [C=trauma-exposed (no PTSD) vs trauma-exposed PTSD (human)] is captured by the 'control type' variable (with levels unexposed, shamexposed, trauma exposed).

[A= non-exposed vs trauma-exposed PTSD (human); B=non-exposed vs trauma exposed no PTSD (human); C=trauma-exposed (no PTSD) vs trauma-exposed PTSD (human); D=non-exposed vs trauma-exposed (no PTSD checked) (animal); E=non-exposed vs trauma-exposed PTSD (animal); F=trauma-exposed (no ptsd) vs trauma-exposed PTSD (animal)]
```{r}
data.explore %>% 
  filter(subject.cat == "Human") %>% 
  filter(comparison != "B") %>% 
  select(-c(rhythm, subject.cat, comparison)) %>%
  droplevels() ->clinical
saveRDS(clinical, file='processed_data/clinical.data.explorative.RDS')
```

Comparison D is included in the preclinical dataset, as most datapoints come from comparison D and we want to explore the influence of this experimental variation. 
D=non-exposed vs trauma-exposed (no PTSD checked) (animal); E=non-exposed vs trauma-exposed PTSD (animal); F=trauma-exposed (no ptsd) vs trauma-exposed PTSD (animal)]
```{r}
data.explore %>% 
  filter(subject.cat == "Animal") %>% 
  select(-subject.cat) %>%
  droplevels() ->preclinical
saveRDS(preclinical, file='processed_data/preclinical.data.explorative.RDS')
```


# MetaForest Clinical
```{r}
set.seed(12345) # set seed to a random number
# Set up k-fold grouped CV
fit_control.clinical <- trainControl(method = "cv", number = 10, index = groupKFold(clinical$new.idPTSD, k = 10))
# Set up a custom tuning grid for the three tuning parameters of MetaForest
rf_grid <- expand.grid(whichweights = c("random", "fixed", "unif"),
                       mtry = c(2, 4, 6),
                       min.node.size = c(2, 4, 6))
set.seed(12345)
# Train the model
cv.mf.cluster.clinical <- train(y = clinical$yi, x = clinical[names(clinical) !="yi"], #from x remove yi
                                study = "new.idPTSD", 
                                method = ModelInfo_mf(), #= method from metaforest. https://rdrr.io/cran/metaforest/man/MetaForest.html
                                trControl = fit_control.clinical,
                                tuneGrid = rf_grid,
                                num.trees = 500, # same var imp & convergencemet 1000 tree
                                data=clinical)
saveRDS(cv.mf.cluster.clinical,file="processed_data/fitted.clinicalMetaForest.RDS") # save object
# readRDS(file="processed_data/fitted.clinicalMetaForest.RDS")->cv.mf.cluster.clinical # to load later and save computation time
```

## Tuning parameters
```{r}
cv.mf.cluster.clinical
```

```{r}
plot(cv.mf.cluster.clinical) # 
```

## Model convergence
```{r}
tiff(file="results/metaforest_Clinical_convergence.tiff", height=800, width=800, pointsize = 8, res=300)
plot(cv.mf.cluster.clinical$finalModel) + theme_pubr(base_size = 8)
dev.off()
```

## Model summary
```{r}
summary(cv.mf.cluster.clinical)
```

## Cross validated R2 with SD
```{r }
cv.mf.cluster.clinical$results[which(cv.mf.cluster.clinical$results$whichweights == "fixed" & 
                                       cv.mf.cluster.clinical$results$mtry == 2 & 
                                       cv.mf.cluster.clinical$results$min.node.size == 6),] # details with the "best" model
```

## Variable importance Plot
```{r}
VarImpPlot(cv.mf.cluster.clinical$finalModel) -> var.imp.plot.clinical
tiff(file="results/metaforest_Clinical_varImportance.tiff", height=1000, width=1000, pointsize=8, res=300) # save plot
var.imp.plot.clinical+  theme_pubr(base_size = 8)
dev.off()

var.imp.plot.clinical+  theme_pubr(base_size = 12) # show plot
```
Note: negative variable importance (in metaforest) ~ just no relation to outcome http://developmentaldatascience.org/post/29-01-18_metaforest_no_effect/


# MetaCART clinical
Only 8% variance explained by MetaForest and PD plots indicate no strong moderators, therefor no MetaCART follow-up analyses performed.


# PD plots clinical
Select variables for PD plots
```{r}
# https://www.rdocumentation.org/packages/metaforest/versions/0.1.3
varImp(cv.mf.cluster.clinical,scale = F) ->imp.scores.clinical

# export variable importance scores (ordered) to csv
imp.clinical <- as.data.frame(imp.scores.clinical$importance)
imp.clinical <- data.frame(overall = imp.clinical$Overall,
                           names   = rownames(imp.clinical))
write.csv2(imp.clinical[order(imp.clinical$overall,decreasing = T),],"results/important_variables_clinical_metaforest.csv")

# # select all variables
imp.clinical[order(imp.clinical$overall,decreasing = T),] -> important.vars.clinical
important.vars.clinical$names ->variable.clinical
variable.clinical
```
## Main PD plots
```{r}
# Create PD list
PartialDependence(cv.mf.cluster.clinical$finalModel, vars = variable.clinical,
                  bw=T, rawdata=F, pi = .95, output = 'list'
) ->PD.list.clinical

# change layout (for better readability)
PD.list.clinical %>% 
  map(~.x + labs(x=NULL, y=NULL)) %>% 
  map(~.x + theme_pubr(base_size = 8)) %>%
  map(~.x + theme(axis.text.x = element_text(angle = 45,hjust = 1,vjust = 1))) %>%
  map(ggplotGrob) ->grobz.clinical

  # https://stackoverflow.com/questions/35068129/arrange-ggplot-plots-grobs-with-same-widths-using-gtable-to-create-2x2-layout
  {arrangeGrob(grobs=grobz.clinical, 
              ncol=4,
              left="Hedge's G", bottom = "Variable levels")->PD.clinical # https://community.rstudio.com/t/common-axis-title-in-grid-arrange/96353/2
  grid.newpage()
  grid.draw(PD.clinical)
  }

{tiff(file="results/metaforest_PD_clinical.tiff", height = 2000, width = 3000, res=300) # Higher quality output
  grid.draw(PD.clinical)
  dev.off()}
```


# MetaForest: Preclinical
```{r}
set.seed(94372) #set seeds to a random number
# Set up k-fold grouped CV
fit_control.preclinical <- trainControl(method = "cv", number = 10, index = groupKFold(preclinical$new.idPTSD, k = 10))
set.seed(94372)
# Train the model
cv.mf.cluster.preclinical <- train(y = preclinical$yi, x = preclinical[names(preclinical) !="yi"], #from x remove yi
                                   study = "new.idPTSD", 
                                   method = ModelInfo_mf(), #= method from metaforest. https://rdrr.io/cran/metaforest/man/MetaForest.html
                                   trControl = fit_control.preclinical,
                                   tuneGrid = rf_grid,
                                   num.trees = 500,
                                   data=preclinical)

saveRDS(cv.mf.cluster.preclinical,file="processed_data/fitted.preclinicalMetaForest.RDS") # Save object
# readRDS(file="processed_data/fitted.preclinicalMetaForest.RDS")->cv.mf.cluster.preclinical # to load later and save computation time 
```

## Tuning parameters
```{r}
cv.mf.cluster.preclinical
```

```{r}
plot(cv.mf.cluster.preclinical)
```

## Model convergence
```{r}
tiff(file="results/metaforest_Preclinical_convergence.tiff", height=800, width=800, pointsize=8, res=300)
plot(cv.mf.cluster.preclinical$finalModel)+ theme_pubr(base_size = 8)
dev.off()
```

## Model summary
```{r}
summary(cv.mf.cluster.preclinical)
```

## Cross validated R2 with SD
```{r }
cv.mf.cluster.preclinical$results[which(cv.mf.cluster.preclinical$results$whichweights == "random" & 
                                          cv.mf.cluster.preclinical$results$mtry == 6 & 
                                          cv.mf.cluster.preclinical$results$min.node.size == 2),] # details with the "best" model
```

## Variable importance
```{r}
VarImpPlot(cv.mf.cluster.preclinical$finalModel) ->var.imp.plot.preclinical
tiff(file="results/metaforest_Preclinical_varImportance.tiff", height=1000, width=1000, pointsize=8, res=300) # save plot
var.imp.plot.preclinical +  theme_pubr(base_size = 8)
dev.off()

var.imp.plot.preclinical +  theme_pubr(base_size = 12) # show plot
```


# MetaCART Preclinical
```{r metaCART preclinical, warning=FALSE}
colnames(preclinical)[which(!colnames(preclinical) %in% c("yi", "vi", "new.idPTSD"))] ->p.vars
paste("yi ~", paste(p.vars,collapse="+")) ->p.vars.form

set.seed(38923)
REmrt(formula(p.vars.form),
      vi = vi, data = preclinical, 
      c=0.5,
      maxL=10,
      xval=10,
      lookahead = T
)->REtree.P

saveRDS(REtree.P, "processed_data/REtree.P.rds") # save object
# readRDS("processed_data/REtree.P.rds")->REtree.P # to load later, and save computation time
```

inspect warnings
```{r}
REtree.P$initial.tree  # eerste split is NA
```

```{r }
summary(REtree.P)
```

```{r }
plot(REtree.P)
```

```{r}
tiff(file="results/metaCART.preclinical.tiff", height = 3000, width = 3000, res=300, pointsize = 12)
plot(REtree.P)
dev.off()
```


# PD plots preclinical
```{r}
# https://www.rdocumentation.org/packages/metaforest/versions/0.1.3
varImp(cv.mf.cluster.preclinical,scale = F) ->imp.scores.preclinical

# export variable importance scores (ordered) to csv
imp.preclinical <- as.data.frame(imp.scores.preclinical$importance)
imp.preclinical <- data.frame(overall = imp.preclinical$Overall,
                              names   = rownames(imp.preclinical))
write.csv2(imp.preclinical[order(imp.preclinical$overall,decreasing = T),],"results/important_variables_preclinical_metaforest.csv")

# select all variables
imp.preclinical[order(imp.preclinical$overall,decreasing = T),] -> important.vars.preclinical
important.vars.preclinical$names ->variable.preclinical
variable.preclinical
```

## Main PD plots
```{r}
PartialDependence(cv.mf.cluster.preclinical$finalModel, vars = variable.preclinical, bw=T, rawdata=F, pi = .95, output = 'list') ->PD.list.preclinical

# change layout  (for better readability)
PD.list.preclinical %>% 
  map(~.x + labs(x=NULL, y=NULL)) %>% 
  map(~.x + theme_pubr(base_size = 8)) %>%
  map(~.x + theme(axis.text.x = element_text(angle = 45,hjust = 1,vjust = 1))) %>%
  map(ggplotGrob) ->grobz.preclinical # remove y pabs

{
  arrangeGrob(grobs=grobz.preclinical, 
              ncol=4, #nrow=4, 
              left="Hedge's G", bottom = "Variable levels")->PD.preclinical # https://community.rstudio.com/t/common-axis-title-in-grid-arrange/96353/2
  grid.newpage()
  grid.draw(PD.preclinical)
}

{tiff(file="results/metaforest_PD_preclinical.tiff", height = 3000, width = 3000, res=300) # Higher quality output
  grid.draw(PD.preclinical)
  dev.off()}
```

## PD plot with metaCART interactions
```{r}
PartialDependence(cv.mf.cluster.preclinical$finalModel, 
                  vars=c("ptsd.type", "phase"), moderator = "information.type", 
                  bw=F, rawdata=F, pi = .95, output = 'list')->PD.list.preclinical.metacart

PD.list.preclinical.metacart %>% 
  map(~.x + labs(x=NULL, y=NULL)) %>% 
  map(~.x + theme_pubr(base_size = 8)) %>%
  map(~.x + theme(axis.text.x = element_text(angle = 45,hjust = 1,vjust = 1))) %>%
     map(~.x + scale_color_viridis (discrete = TRUE, #begin = 0.1, end = 0.9 , 
                          option = "cividis") ) %>% 
  map(ggplotGrob) ->grobz.preclinical.metacart # remove y pabs

{arrangeGrob(grobs=grobz.preclinical.metacart,
              ncol=2,
              left="Hedge's G", bottom = "Variable levels")->PD.preclinical.metacart # https://community.rstudio.com/t/common-axis-title-in-grid-arrange/96353/2
  grid.newpage()
  grid.draw(PD.preclinical.metacart)
}

{tiff(file="results/metaforest_PD_preclinical_metaCARTfollowup.tiff", height = 1000, width = 2500, res=300) # Higher quality output
  grid.draw(PD.preclinical.metacart)
  dev.off()}
```


# Combine plots preclinical and clinical
```{r}
ggarrange(
  var.imp.plot.clinical + labs(title = "A) Clinical data") + theme_pubr(base_size = 8),
  var.imp.plot.preclinical + labs(title = "B) Preclinical data") + theme_pubr(base_size = 8) + rremove("ylab"),
  ncol =2, nrow=1
) ->var.imp.plots
var.imp.plots
```

## Save Var imp clinical and preclinical data together
```{r}
ggsave("results/VarImp.clinical.preclinical.tiff", 
       plot=var.imp.plots,
       device="tiff", dpi = 300, height = 3, width = 7, limitsize = T )
```