---
title: "Prepare QA"
author: "Milou Sep"
date: "4/15/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
rm(list = ls()) #clean environment
# load files from OSF
library(osfr)
# Authenticate to OSF (see: http://centerforopenscience.github.io/osfr/articles/auth.html). Via osf_auth("PAT") in the commentline. (note PAT can be derived from OSF)

library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)


```

# retrieve OSF files 
```{r}
osf_retrieve_file("tckb5") %>% osf_download(path = "data", conflicts="overwrite") # QA data
```

# load animal / preclinical data
```{r}
A1 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_search1")
# str(A1)                 
A1 = A1[-1,] # drop first row is sort of extra header

A2 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_search2")
A2 = A2[-1,] # drop first row is sort of extra header
# str(A2)

A3 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_search3")
A3 = A3[-1,] # drop first row is sort of extra header
# str(A3)
```

merge animal
```{r}
bind_rows(list(A1, A2, A3),.id="s") %>%
  select(-c(Reference, notes))-> QA.A # When row-binding, columns are matched by name, and any missing columns will be filled with NA.
head(QA.A)
```

# load human / clinical data
```{r}
H1 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_search1")
H1 = H1[-1,] # drop first row is sort of extra header

H2 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_search2")
H2 = H2[-1,] # drop first row is sort of extra header
# str(H2)

H3 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_search3")
H3 = H3[-1,] # drop first row is sort of extra header
# str(H3)
```

merge human
```{r}
bind_rows(list(H1, H2, H3),.id="s") %>%
  select(-c(Reference, notes))-> QA.H # When row-binding, columns are matched by name, and any missing columns will be filled with NA.
head(QA.H)
```

# Recode data

# Note: for QA score -> higher is better quality.
Y=0; N=1; unclear =1/2

"valeria: "for sensitivity analysis, amount of potential bias was operationalized by summing the risk of bias of each item according to the definition: “yes” = 0, “unclear” = 0.5, “no” = 1."

## Clinical
```{r}
glimpse(QA.H)
Hcode <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_coding")

QA.H %>% 
  mutate_at( .vars=(Hcode$var[1:8]), ~substr(.,1,1)) %>%
  mutate_at(.vars=(Hcode$var[1:8]), ~case_when(
    grepl("Y|y",.) ~"0",  # NB yes is low risk of bias
    grepl("N|n",.) ~ "1", # NB no is high risk of bias
    grepl("U|u",.) ~ "0.5")) %>%
  mutate_at( .vars=(Hcode$var[1:8]), as.numeric) %>%
  mutate(RoB_score = select(.,Hcode$var[1:8]) %>% rowSums()) %>%
  mutate_at( .vars=(Hcode$var[1:8]), factor) %>%
  filter(RoBQA_NOS_S1_validPTSD == 0)->QA.H.recoded

# checks
head(QA.H.recoded)
is.na(QA.H.recoded) %>% any()#should be non
```

## preclinical
```{r}
glimpse(QA.A)
Acode <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_coding")

Acode$var[1:10] # including extra measures
Acode$var[1:8] # only SYRCLE rob

QA.A %>% 
  mutate_at( .vars=(Acode$var[1:10]), ~substr(.,1,1)) %>%
  mutate_at(.vars=(Acode$var[1:10]), ~case_when(
    grepl("Y|y",.) ~"0",  # NB yes is low risk of bias
    grepl("N|n",.) ~ "1", # NB no is high risk of bias
    grepl("U|u",.) ~ "0.5")) %>% 
  mutate_at( .vars=(Acode$var[1:10]), as.numeric) %>%
  mutate(RoB_score = select(.,Acode$var[1:8]) %>% rowSums()) %>%
  mutate_at( .vars=(Acode$var[1:8]), factor) %>%
  filter(RoBQA_extra_validModel == 0 & RoBQA_extra_behavioralTask == 0) %>%
  select(-c("RoBQA_extra_validModel", "RoBQA_extra_behavioralTask"))->QA.A.recoded

#checks
head(QA.A.recoded)

# QA.A.recoded
is.na(QA.A.recoded) %>% any() # should be non
```

# save recoded datafiles
```{r}
saveRDS(QA.A.recoded, file = "processed_data/TRACE_QA_animal.RData")
saveRDS(QA.H.recoded, file = "processed_data/TRACE_QA_human.RData")
```


## Visualize study quality

### Clinical data
```{r}
pivot_longer(QA.H.recoded, cols = grep("RoBQA",names(QA.H.recoded)), names_to = "question", values_to = "score") %>%
  count(question, score) %>%
  mutate(
    question = factor(question, levels = c(
      "RoBQA_NOS_S1_validPTSD", "RoBQA_NOS_S2_repCase", "RoBQA_NOS_S3_repControl", "RoBQA_NOS_S4_defControl", 
      "RoBQA_NOS_C_confounders", "RoBQA_NOS_E1_outcome", "RoBQA_NOS_E2_sameOut", "RoBQA_NOS_E3_nonRep"
    ),
    labels = c("PTSD measure (S1)", "representative PTSD subjects (S2)", "representative control subjects (S3)", "control definition (S4)",
               "adjustments for confounders (C)", "behavioural measure (E1) ", "same task case control (E2)", "same non-response rate (E3)"
    )
    ), # reorder levels
    score=factor(score, levels = c("0","0.5","1"),  # Y=0=low risk, N=1=high risk
                 labels=c("Low RoB", "Unclear", "High RoB"))
  ) -> QA.H.recoded.long

QA.H.recoded %>% head()
QA.H.recoded.long %>% head()

# https://www.r-graph-gallery.com/48-grouped-barplot-with-ggplot2.html
ggplot(QA.H.recoded.long, aes(fill=score, x=n, y=question)) + 
  geom_bar(position="fill", stat="identity",   # fill displays percentages (or proportion)
           aes(
             y = reorder(question, desc(question)),
              fill = reorder(score, desc(score)) 
           ) # reorder factor levels
  ) +
  scale_x_continuous(labels=c("0%", "25%", "50%", "75%", "100%"))+
  labs(x="", y="", title="Clinical studies"
       #subtitle = "Clinical studies"
  )+
  scale_fill_brewer(palette = "BuGn", direction = 1)+
  
  theme_minimal() +
  theme(legend.title = element_blank())->RoB.clincal
RoB.clincal
```

```{r eval=FALSE, include=FALSE}
ggsave("results/RoB_clinical.jpeg",plot=RoB.clincal,width = 15, height = 10, units = "cm")
```


### Preclinical data
```{r}
pivot_longer(QA.A.recoded, cols = grep("RoBQA",names(QA.A.recoded)), names_to = "question", values_to = "score") %>%
  count(question, score) %>%
  mutate(
    question = factor(question, levels = c(
      "RoBQA_syrcle_1_seqGeneration", "RoBQA_syrcle_2_baseline", "RoBQA_syrcle_3_allocation", "RoBQA_syrcle_4_housing", 
      "RoBQA_syrcle_5_blindExp", "RoBQA_syrcle_6_outAss", "RoBQA_syrcle_7_outBlind", "RoBQA_syrcle_8_incData"
    ),
    labels = c("sequence generation (1)", "baseline characteristics (2)", "allocation concealment (3)", "random housing (4)",
               "blinding experimenter (5)", "random outcome assessment (6) ", "blinded outcome assessment (7)", "incomplete data adequatly addressed (8)"
    )
    ), # reorder levels
    score=factor(score, levels = c("0","0.5","1"),  # Y=0=low risk, N=1=high risk
                 labels=c("Low RoB", "Unclear", "High RoB"))
  ) -> QA.A.recoded.long

QA.A.recoded %>% head()
QA.A.recoded.long %>% head()
# str(QA.A.recoded.long)

# https://www.r-graph-gallery.com/48-grouped-barplot-with-ggplot2.html
ggplot(QA.A.recoded.long, aes(fill=score, x=n, y=question)) + 
  geom_bar(position="fill", stat="identity",   # fill displays percentages (or proportion)
           aes(
             y = reorder(question, desc(question)),
              fill = reorder(score, desc(score)) 
           ) # reorder factor levels
  ) +
  scale_x_continuous(labels=c("0%", "25%", "50%", "75%", "100%"))+
  labs(x="", y="", title="Preclinical studies"
       #subtitle = "Preclinical studies"
  )+
  # scale_fill_brewer(palette = "Blues", direction = 1)+
    scale_fill_brewer(palette = "BuGn", direction = 1)+
  
  theme_minimal() +
  theme(legend.title = element_blank()) -> RoB.preclincal
RoB.preclincal
```

```{r eval=FALSE, include=FALSE}
ggsave("results/RoB_preclinical.jpeg",plot=RoB.preclincal,width = 15, height = 10, units = "cm")
```


# save together

```{r}
ggarrange(
  RoB.clincal,
  RoB.preclincal,
  ncol=1, nrow=2,
  align = "v",
  common.legend = T,
  # labels = c("Clinical studies", "Preclinical studies"),
  #  font.label = list(size = 12, color = "black", face = "bold", family = NULL)
  legend="bottom"
)->ROB.plot
ROB.plot
ggsave("results/RoB.jpeg",plot=ROB.plot,width = 12, height = 12, units = "cm")
```
