---
title: "Prepare QA"
author: "Milou Sep"
date: "4/15/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls()) #clean environment
# load files from OSF
library(osfr)
# Authenticate to OSF (see: http://centerforopenscience.github.io/osfr/articles/auth.html). Via osf_auth("PAT") in the comment line. (note PAT can be derived from OSF)
library(readxl)
library(dplyr)
library(tidyr)
```

# retrieve OSF files 
```{r include=FALSE}
osf_retrieve_file("tckb5") %>% osf_download(path = "data", conflicts="overwrite") # QA data
```

# load animal / preclinical data
```{r}
A1 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_search1")
# str(A1)                 
A1 = A1[-1,] # drop first row is sort of extra header

A2 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_search2")
A2 = A2[-1,] # drop first row is sort of extra header
# str(A2)

A3 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_search3")
A3 = A3[-1,] # drop first row is sort of extra header
# str(A3)
```

merge animal
```{r}
bind_rows(list(A1, A2, A3),.id="s") %>%
  select(-c(Reference, notes))-> QA.A # When row-binding, columns are matched by name, and any missing columns will be filled with NA.
head(QA.A)
```

# load human / clinical data
```{r}
H1 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_search1")
H1 = H1[-1,] # drop first row is sort of extra header

H2 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_search2")
H2 = H2[-1,] # drop first row is sort of extra header
# str(H2)

H3 <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_search3")
H3 = H3[-1,] # drop first row is sort of extra header
# str(H3)
```

merge human
```{r}
bind_rows(list(H1, H2, H3),.id="s") %>% select(-c(Reference, notes))-> QA.H # When row-binding, columns are matched by name, and any missing columns will be filled with NA.
head(QA.H)
```

# Recode data

# Note: for QA score -> higher is better quality.
Y=0; N=1; unclear =1/2

Bonapersona V, Kentrop J, Van Lissa CJ, van der Veen R, Joëls M, Sarabdjitsingh RA. The behavioral phenotype of early life adversity: A 3-level meta-analysis of rodent studies. Neurosci Biobehav Rev. 2019 Jul;102:299-307. doi: 10.1016/j.neubiorev.2019.04.021. Epub 2019 Apr 29. PMID: 31047892.
-> "for sensitivity analysis, amount of potential bias was operationalized by summing the risk of bias of each item according to the definition: “yes” = 0, “unclear” = 0.5, “no” = 1."

## Clinical
```{r}
glimpse(QA.H)
Hcode <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_human_coding")

QA.H %>% 
  mutate_at( .vars=(Hcode$var[1:8]), ~substr(.,1,1)) %>%
  mutate_at(.vars=(Hcode$var[1:8]), ~case_when(
    grepl("Y|y",.) ~"0",  # NB yes is low risk of bias
    grepl("N|n",.) ~ "1", # NB no is high risk of bias
    grepl("U|u",.) ~ "0.5")) %>%
  mutate_at( .vars=(Hcode$var[1:8]), as.numeric) %>%
  mutate(RoB_score = select(.,Hcode$var[1:8]) %>% rowSums()) %>%
  mutate_at( .vars=(Hcode$var[1:8]), factor) %>%
  filter(RoBQA_NOS_S1_validPTSD == 0)->QA.H.recoded

# checks
head(QA.H.recoded)
is.na(QA.H.recoded) %>% any() # confirm no missing values
```

## preclinical
```{r}
glimpse(QA.A)
Acode <- read_excel("data/TRACE_RoBQA_data.xlsx", sheet = "RoBQA_animal_coding")

Acode$var[1:10] # including extra measures
Acode$var[1:8] # only SYRCLE rob

QA.A %>% 
  mutate_at( .vars=(Acode$var[1:10]), ~substr(.,1,1)) %>%
  mutate_at(.vars=(Acode$var[1:10]), ~case_when(
    grepl("Y|y",.) ~"0",  # NB yes is low risk of bias
    grepl("N|n",.) ~ "1", # NB no is high risk of bias
    grepl("U|u",.) ~ "0.5")) %>% 
  mutate_at( .vars=(Acode$var[1:10]), as.numeric) %>%
  mutate(RoB_score = select(.,Acode$var[1:8]) %>% rowSums()) %>%
  mutate_at( .vars=(Acode$var[1:8]), factor) %>%
  filter(RoBQA_extra_validModel == 0 & RoBQA_extra_behavioralTask == 0) %>%
  select(-c("RoBQA_extra_validModel", "RoBQA_extra_behavioralTask"))->QA.A.recoded

#checks
head(QA.A.recoded)
is.na(QA.A.recoded) %>% any() # confirm no missing values
```

# save recoded datafiles
```{r}
saveRDS(QA.A.recoded, file = "processed_data/TRACE_QA_animal.RData")
saveRDS(QA.H.recoded, file = "processed_data/TRACE_QA_human.RData")
```