---
title: "recode variables"
author: "Milou Sep"
date: "4/13/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls()) #clean environment
library(readxl)
library(dplyr)

library(osfr) # to download method codes
```

```{r}
readRDS("processed_data/TRACEmerged.RDS")->merged.data

 # data<-readRDS("processed_data/TRACErecoded.RDS") # contains only included, recoded, data 
 #data <- read.csv("processed_data/TRACEmerged.csv", sep = ";", dec = c(",", ".")) # Data

 osf_retrieve_file("a6dmj") %>% osf_download(path = "data", conflicts="overwrite") # search 3
 method <- read_excel("data/TRACE_method_codes.xlsx", sheet = "codes")
# method <- read.csv("TRACE_method_codes.csv", sep = ";", na.strings = c(" ", "-"), dec = c(",", ".")) # Method codes

 method %>% select(!notes) %>% filter(is.na(.)) # check, should be no missing.
 # Select relevant colums dataset
method %>% select(task, measure, type, phase, valence, recode, cuectx) -> method 
# Create reference var as character
merged.data1<-merged.data %>% mutate(reference = as.character(paste(author, year, sep=" "))) %>% select(-c(author, year)) # Merge year & author & dropvars.
```



# select only inclusions (only this data double checked in recoding vars etc)
```{r}
merged.data1 %>% filter(decision == 1) %>% select(-decision) %>% droplevels() -> merged.inclusions
```


## Add method codes to data
NB the combination of task and measure indicates which method is used to measure behavior. Those values are combined into a new variable ..
```{r}
merged.inclusions %>% mutate(measureID = as.factor(paste(task, measure, sep="."))) -> merged.inclusions.A
method %>% mutate(measureID = as.factor(paste(task, measure, sep="."))) -> method1
#' ... that is used to merge data and method codes
# df4<- merge(df3, method1, by="measureID", all=T, suffixes = c("_d", "_m"))

left_join(merged.inclusions.A ,method1, by="measureID", suffix = c(".d", ".m"))->merged.inclusions.B

# glimpse(df4)

#' Quality check after merging.. (should be identical)
 identical(as.character(merged.inclusions.B$task.d), as.character(merged.inclusions.B$task.m))
 identical(as.character(merged.inclusions.B$measure.d), as.character(merged.inclusions.B$measure.m))
# dat %>% select(-c(task_m, measure_m)) -> dat #remove duplicate colums (niet echt nodig...)
```


# Recoding Subject variables

## Age: set age groups

subject:
(0=humanmixed(Civiel&Military); 1=ActiveDutyMilitary; 2=Veteran; 12=ActiveDutyMilitary & Veteran; 3=Civilian; 4=Rat; 5=Mice)

refs for age groups
- [https://www.jax.org/news-and-insights/jax-blog/2017/november/when-are-mice-considered-old#]
- [https://www.jax.org/news-and-insights/jax-blog/2017/november/when-are-mice-considered-old#] (based on C557BL/6J)
- [https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3733029/[ table 2]

- week month calculations
https://www.google.com/search?q=2+months+weeks&oq=2+months+weeks&aqs=chrome..69i57j0i22i30l3.1762j0j4&sourceid=chrome&ie=UTF-8

```{r}
merged.inclusions.B %>% mutate(
  
  # ptsd age
  age.PTSD2 = as.numeric(age.PTSD),
  age.PTSD.cat = case_when(
    age.PTSD == 'adult'~'(mature) adult',
    #human
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 < 20) ~ "young adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 >= 20 & age.PTSD2 <35) ~ "(mature) adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 >=35  & age.PTSD2 <50) ~ "middle-aged",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.PTSD2 >=50) ~ "old adult",
    # rat
    (subject == "4") & (age.PTSD2 < 26) ~ "young adult", # < 6months ~ 26.0715 weeks
    (subject == "4") & (age.PTSD2 >= 26 & age.PTSD2 <52) ~ "(mature) adult", # 6 months - 12 months (= 52)
    (subject == "4") & (age.PTSD2 >= 52 & age.PTSD2 <78) ~ "middle-aged", # 12 months - 18 months (= 78)
    (subject == "4") & (age.PTSD2 >=78) ~ "old adult",
    # mice
    (subject == "5") & (age.PTSD2 < 13) ~ "young adult", # 3 months
    (subject == "5") & (age.PTSD2 >= 13 & age.PTSD2 <26) ~ "(mature) adult", # 3-6 months
    (subject == "5") & (age.PTSD2 >= 26 & age.PTSD2 <60) ~ "middle-aged", # 10 - 14 months -> 6 - 14 (60 weeks)
    (subject == "5") & (age.PTSD2 >=60) ~ "old adult" 
  ),
  
  # HC
  age.HC2 = as.numeric(age.HC),
  age.HC.cat = case_when(
    age.HC == 'adult'~'(mature) adult',
    #human
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 < 20) ~ "young adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 >= 20 & age.HC2 <35) ~ "(mature) adult",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 >=35  & age.HC2 <50) ~ "middle-aged",
    (subject %in% c("0", "1", "2", "12", "3")) & (age.HC2 >=50) ~ "old adult",
    
    # rat
    (subject == "4") & (age.HC2 < 26) ~ "young adult", # < 6months ~ 26.0715 weeks
    (subject == "4") & (age.HC2 >= 26 & age.HC2 <52) ~ "(mature) adult", # 6 months - 12 months (= 52)
    (subject == "4") & (age.HC2 >= 52 & age.HC2 <78) ~ "middle-aged", # 12 months - 18 months (= 78)
    (subject == "4") & (age.HC2 >=78) ~ "old adult",
    
    # mice
    (subject == "5") & (age.HC2 < 13) ~ "young adult", # 3 months
    (subject == "5") & (age.HC2 >= 13 & age.HC2 <26) ~ "(mature) adult", # 3-6 months
    (subject == "5") & (age.HC2 >= 26 & age.HC2 <60) ~ "middle-aged", # 10 - 14 months -> 6 - 14 (60 weeks)
    (subject == "5") & (age.HC2 >=60) ~ "old adult" 
  )
  
)-> merged.inclusions.recoded
```


no missing values after recoding age in included papers
```{r eval=FALSE, include=FALSE}
merged.inclusions.recoded %>% select(subject, age.PTSD, age.PTSD2, age.PTSD.cat,
                               age.HC, age.HC2, age.HC.cat) %>% filter(is.na(.))
```


```{r eval=FALSE, include=FALSE}
merged.inclusions.recoded %>% filter(age.PTSD2 > 65)%>% View()
merged.inclusions.recoded %>% filter(age.HC2 > 65)  %>% View()
```

```{r}
 merged.inclusions.recoded %>% select(!c(age.PTSD, age.PTSD2, age.HC, age.HC2))-> merged.inclusions.recoded2
```


## Day/Night rhytem

```{r}
merged.inclusions.recoded2 %>% mutate(rhythm = ifelse(subject %in% c("0", "1", "2", "12", "3"),"active", rhythm)) -> merged.inclusions.recoded3
merged.inclusions.recoded3$rhythm <- recode(merged.inclusions.recoded3$rhythm, 'dark' = 'active', 'light' = 'inactive')
# for checking
merged.inclusions.recoded3 %>%  filter(is.na(rhythm)) # good
```


## Time since trauma
```{r}
merged.inclusions.recoded3 %>% 
  mutate( 
    #sort year/month/day in new vars
    time.year = ifelse(grepl("year", time), yes=time, no=NA),
    time.month = ifelse(grepl("month", time), yes=time, no=NA),
    time.day= ifelse(grepl("day", time), yes=time, no=NA),
    # remove day/month/year text
    time.year2 = sub("year|years", "",time.year),
    time.month2 = sub("month|months", "",time.month),
    time.day2 = sub("day|days", "",time.day),
    # remove > ?signs
    time.year3 = sub(">|<", "",time.year2),
    time.month3 = sub(">|<", "",time.month2),
    time.day3 = sub(">|<", "",time.day2),
    # recode decimal sign , to . (otherwise NA after 'as.numeric', likely due to leading 0'zs etc)
    time.year4 = sub(",", ".",time.year3),
    time.month4 = sub(",", ".",time.month3),
    time.day4 = sub(",", ".",time.day3)
    
  )-> merged.inclusions.recoded4

# for checking
# merged.inclusions.recoded4  %>% select(time, time.year, time.year2, time.year3,time.year4,
#                                        time.month,time.month2,time.month3,time.month4,
#                                        time.day,time.day2, time.day3, time.day4) %>% View() 

# for checking
# glimpse(merged.inclusions.recoded4)
# merged.inclusions.recoded4$time.year4 %>% as.numeric()

merged.inclusions.recoded4 %>% 
  mutate(time.recoded = case_when(
      # human all to years
      (subject %in% c("0", "1", "2", "12", "3")) & (grepl("year", time, ignore.case = T)) ~ as.numeric(time.year4),
      (subject %in% c("0", "1", "2", "12", "3")) & (grepl("month", time, ignore.case = T)) ~ (as.numeric(time.month4) / 12),
      # rat & mice all to days
      (subject %in% c("4", "5")) & (grepl("day", time, ignore.case = T)) ~ as.numeric(time.day4),
      (subject %in% c("4", "5")) & (grepl("month", time, ignore.case = T)) ~ (as.numeric(time.month4) * 30.4)),
#https://www.google.com/search?q=months+to+years&oq=months+to+&aqs=chrome.0.0l3j69i57j0l6.2154j0j7&sourceid=chrome&ie=UTF-8

# All to pseudo-years
#     - omrekenen tijd in mens, rat en muis
# 	- in adulthood: 11.8 rat days = 1 human year [https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3733029/]
# 	- in adulthood: 2.60 mice day = 1 human year  [https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3733029/]

time.pseudo = case_when(
  (subject %in% c("0", "1", "2", "12", "3")) ~ as.numeric(time.recoded),
  #rat
  (subject == "4") ~ (as.numeric(time.recoded)/11.8),
  #mice
  (subject == "5") ~ (as.numeric(time.recoded)/2.60)
)
) -> merged.inclusions.recoded5

# for checking
# merged.inclusions.recoded5 %>% 
#   select(subject, time, time.year, time.year2, time.year3,
#                time.month,time.month2,time.month3,
#                time.day,time.day2, time.day3,
#                time.recoded, time.pseudo) %>% 
#   # filter(subject == "5") %>%
#   # str(time.recoded)
#    filter(is.na(time.pseudo)) %>%
#   # (filter(time == "unclear")) %>% 
#   View() # correct

# merged.inclusions.recoded5 %>% filter(subject == "4")

merged.inclusions.recoded5 %>% select(-c(time.year, time.month, time.day, time.year2, time.month2, time.day2, time.year3, time.month3, time.day3, time.year4, time.month4, time.day4, time.recoded)) -> merged.inclusions.recoded6
```

## Subject: new Human-Animal variable
```{r}
merged.inclusions.recoded6 %>% mutate(subject.cat = ifelse(subject %in% c("0", "1", "2", "12", "3"), "Human", "Animal")) ->merged.inclusions.recoded7
```

## recode control type
```{r}
merged.inclusions.recoded7$control.type = recode(merged.inclusions.recoded7$control.type, "Handled" = "UnExp")
```




## Check missing values
```{r}
which(is.na(merged.inclusions.recoded7$subject.cat))
```


```{r}
which(is.na(merged.inclusions.recoded7$PMID))
```


```{r}
which(is.na(merged.inclusions.recoded7$comparison))
```


## recode measure, PTSD type and population
```{r}

# df4$subject.cat

# df4.1 %>% select(subject.cat, measure.d, measure2, ptsd.type, ptsd.type2, population, population2) %>% View()


merged.inclusions.recoded7 %>% mutate(
  measure2 = case_when(
    # measure
    (subject.cat == "Animal") & grepl("freezing", measure.d, ignore.case = T) ~ "freezing",
    (subject.cat == "Animal") & grepl("latency|exploration|time|entrie|avoidance|cross|error|DR|DI", measure.d, ignore.case = T) ~ "exploration",
    (subject.cat == "Animal") & grepl("Object", measure.d, ignore.case = T) ~ "manipulation",
    # human
    (subject.cat == "Human") & grepl("EMG|SCR", measure.d, ignore.case = T) ~ "physiology",
    (subject.cat == "Human") & !grepl("EMG|SCR", measure.d, ignore.case = T) ~ "non-physiology"),
  # PTSD type
  # ptsd.type2 = ifelse(grepl("Mixed", ptsd.type, fixed = T), "Mixed", as.character(ptsd.type)),
  
  ptsd.type2 = case_when(
    (subject.cat == "Human") & grepl("Mixed", ptsd.type, fixed = T) ~ "Mixed",
    (subject.cat == "Animal") & (grepl("+", ptsd.type, fixed=T) #| grepl("SPS", ptsd.type, fixed=T)
                                 ) ~ "Mixed",
    TRUE ~ as.character(ptsd.type)),
  
  # Population
  population2 = case_when(
    #human
    (subject.cat == "Human") & grepl("Veterans", population, fixed = T) ~ "Veterans",
    (subject.cat == "Human") & grepl("Civilian", population, fixed = T) ~ "Civilian",
    (subject.cat == "Human") & grepl("Refugee", population, fixed = T) ~ "Civilian",
    #animals
    (subject.cat == "Animal") & grepl("C57BL/6", population, fixed = T) ~ "C57BL/6",
    (subject.cat == "Animal") & grepl("Charles Foster", population, fixed = T) ~ "Charles Foster",
    (subject.cat == "Animal") & grepl("Wistar", population, fixed = T) ~ "Wistar",
    TRUE ~ as.character(population))) %>%
    # mutate(
    #   ptsd.type2= as.factor(ptsd.type2),
    #   population2= as.factor(population2)) %>% 
    droplevels()->merged.inclusions.recoded7A

# # for checking
# merged.inclusions.recoded7A %>% 
#   filter(subject.cat == "Human") %>%
#     filter(subject.cat == "Animal") %>%
#   # filter(is.na(measure2)) %>%
#   select(task.d, valence, phase, measure.d, measure2) %>% 
#   # distinct(measure.d) %>%
#    View()
```




## set variable types
         
all are current character
```{r variable types}
names(merged.inclusions.recoded7A) 

string_names <- c("author", "year",
"PMID",
"shocks.num", "shocks.amp",

"idPTSD", "idHC",

"outcomePTSD", "outcomeHC",
"ptsd.measure", 
"task", "measure"
)

factor_names <-c( #"decision", 
                 "subject","subject.cat",
                 "sex.PTSD", "sex.HC",
"ptsd.type", 'control.type', 'population',
"rhythm",

"comparison",
"res.sus.split", "age.PTSD.cat", "age.HC.cat",

# and recoded factors
"ptsd.type2", "population2","task.d", "measure.d", "measure2", "type", "phase", "valence", "cuectx"
)

numeric_names <- c("nPTSD", "nHC", "meanPTSD", "sdPTSD", "semPTSD", "meanHC", "sdHC", "semHC", "time.pseudo")

# For checking -> ok!
# merged.data.recoded2 %>% mutate_at(.vars=numeric_names, as.numeric) %>% filter(decision == 1) %>% select(numeric_names) %>% is.na() %>% View()



merged.inclusions.recoded7A %>% 
mutate_at(.vars=numeric_names, as.numeric) %>% 
mutate_at(.vars=factor_names, factor) ->merged.inclusions.recoded8


# for checking
 # cbind(merged.data.recoded3$nHC,merged.data.recoded4$nHC)
# unique(merged.inclusions.recoded8$author) %>% data.frame() %>%head()
str(merged.inclusions.recoded8)
```

## add factor labels subject
(0=humanmixed(Civiel&Military); 1=ActiveDutyMilitary; 2=Veteran; 12=ActiveDutyMilitary & Veteran; 3=Civilian; 4=Rat; 5=Mice)

```{r}
str(merged.inclusions.recoded8$subject)
merged.inclusions.recoded8$subject = factor(merged.inclusions.recoded8$subject,
                                            levels = c("0", "1", "2", "12", "3", "4", "5"),
                                            labels = c("Mixed", "Military", "Veteran", "Military+Veteran", "Civilian", "Rat", "Mice"))
```


## correct ID coding PTSD and HC groups

If part of the subjects in a experimental/control group is reused, this group must get the same identification code as the complete group (otherwise groups get incorrect unique codes in the analyses). In datafiles currently:

 - [ ] exp & control ID -> als sub group gebruikt is moet die dezelfde code als de totale group hebben, anders krijgen ze unique codes in de analyses (en dat is incorrect ivm nesting)
 - [ ] in S3 correct
 - [ ] animal two exp groups together: "exp ID 355+347"
 - [x] in human all correct
 - [ ] in S1 en S2 heb ik steeds 'part of..' opgeschreven
 - [ ] pas aan in r in S2 animal:
   - [ ] in exp ID: "part of #" en controlID_#
 - [ ] in control ID: "part of #" en "part of exp ID #"
 - [x] s2 human NA
 - [ ] s1 :
   - [ ] in exp ID: "part of #" en ControlID_#
 - [ ] in control ID: "part of exp ID #"
```{r}
merged.inclusions.recoded8 %>% 
  mutate(idPTSD = sub("part of ", "",idPTSD, fixed = TRUE),
         idPTSD = ifelse(idPTSD == "exp ID 355+347", yes = "355", no= idPTSD),
         idHC = sub("part of ", "",idHC, fixed = TRUE)) -> merged.inclusions.recoded9

# for checking
merged.inclusions.recoded9$idPTSD %>% unique()
merged.inclusions.recoded9$idHC %>% unique()
```


## new variables for phase & valence
```{r}
merged.inclusions.recoded9 %>% mutate(
  
  phase.valence = case_when(
    phase == "L" & valence %in% c("N") ~ "LN",
    phase == "M" & valence %in% c("N") ~ "MN",
    
    phase == "L" & valence %in% c("E") ~ "LE",
    phase == "M" & valence %in% c("E") ~ "ME",
    
    phase == "L" & valence %in% c("F") ~ "LF",
    phase == "M" & valence %in% c("F") ~ "MF",
    phase == "E" & valence %in% c("F") ~ "EF",
    
    phase == "L" & valence %in% c("T") ~ "LT",
    phase == "M" & valence %in% c("T") ~ "MT",
    phase == "E" & valence %in% c("T") ~ "ET"), 
  
  phase.valence = factor(phase.valence, 
                          levels=c("LN", "MN", "LE", "ME", "LF", "MF", "EF", "LT", "MT", "ET"), 
                          labels = c("neutral learning", "neutral memory", 
                                     "emotional learning", "emotional memory", 
                                     "fear learning", "fear memory", "fear memory persistence", 
                                     "trauma learning", "trauma memory", "trauma memory persistence")),
  
phase_Grouped = ifelse(phase %in% c("M","E"), "memory", "learning"),
phase_Grouped = factor(phase_Grouped),

Valence_Grouped = ifelse(valence %in% c("T","F","E"), "emotional", "neutral"), #NB nu trauma ook bij emotional!
Valence_Grouped = factor(Valence_Grouped)

) ->merged.inclusions.recoded10

```


```{r save}
saveRDS(merged.inclusions.recoded10, "processed_data/TRACErecoded.RDS")
 # write.csv2(merged.inclusions.recoded8, "processed_data/TRACErecoded.csv", fileEncoding = "UTF-8") # writes spec characters weird
 # write.table(merged.inclusions.recoded8, "processed_data/TRACErecoded.csv") # same problem
```
