---
title: "Theory-driven meta-analysis TRACE"
author: "Milou Sep"
date: "4/15/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Analysis script for TRACE analyses (based on analyses script Valeria (meta behavior))
# Code largely based on // adapted from Bonapersona, V. (2019, May 20). The behavioral phenotype of early life adversity: a 3-level meta-analysis of rodent studies. Retrieved from osf.io/ra947


# Environment Preparation
```{r setup, include=FALSE}
rm(list = ls()) #clean environment
# libraries
library(dplyr) #general
library(ggplot2) #for graphs
library(metafor) #for meta-analysis
library(ggpubr) # To show multiple plots in 1 figure
library(flextable) # to create tables
library(officer)# to export tables to word
```

# import dataset 
(processed with merge_datasets.rmd, recode_merged_data.rmd, add_effect_size_QA.rmd)
```{r}
data<-readRDS("processed_data/TRACEprepared.RData")

```


```{r eval=FALSE, include=FALSE}
data %>% filter(subject.cat =="Human") %>% 
   # filter(comparison !="B") %>%
  droplevels() ->clinical

# data %>% filter( PMID == "19345420")
# clinical %>% filter(valence == "F") ->df1
# unique(df1$PMID)

# clinical$phase.valence

clinical %>% group_by(#subject.cat, #type, 
                  phase.valence, #phase, valence, #cuectx
                  #, measure2, ptsd.type2, population2
                  ) %>%
summarize(papers=length(unique(PMID)), comparisons=length(each)) %>% data.frame()


mod.H <- rma.mv(yi, vi,
                 random = list(~1 | new.idPTSD , ~1 | PMID),  # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
               # random = ~ 1 | new.idPTSD / each,  # identical results as row above  # https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/fitting-a-three-level-model.html
                 # mods   = ~phase.valence - 1,
               # mods = ~Valence_Grouped:phase_Grouped-1, # all impaired
               mods = ~valence:phase-1, # fear ext and fear memory impoved (trauma m NS), rest impaired
                method = "REML",
                slab = clinical$reference,  # from old codes milou (change for author/year)
                data = clinical) # Similar effects with dat2 (trauma learning excluded)
summary(mod.H)

 forest(mod.H, cex = .2)

 clinical %>% filter(yi > 4) %>% View()

clinical %>% filter(measure.d == "EXT_%CS+/maxCS+Acq_EMG") %>% View()


data %>% filter(subject.cat =="Animal") %>% droplevels() ->preclinical
# preclinical %>% filter(valence == "F") ->df13
# df13 %>% select(PMID, task.d, measure.d, idPTSD,idHC, outcomePTSD, outcomeHC) %>% View()

mod.A <- rma.mv(yi, vi,
                random = list(~1 | new.idPTSD , ~1 | PMID), # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                # mods   = ~phase:Valence_Grouped - 1,  # NB only interaction term
                  # mods   = ~phase.valence - 1, #NL & M impaired, rest improved
                 mods = ~valence:phase-1, # identical resuls as above (so recoded var not needed)
                method = "REML",
                slab = preclinical$reference,  # from old codes milou (change for author/year)
                data = preclinical) # Similar effects with dat2 (trauma learning excluded)
summary(mod.A)
```






# Filter data

## Filter data for phase x valence
Excluded phase == extinction and valence == trauma -> to analyze Learning vs Memory & Neutral vs Stressful
Excluded comparison "B": 
 
 # A= non-exposed vs trauma-exposed PTSD (human); B=non-exposed vs trauma exposed no PTSD (human); C=trauma-exposed (noPTSD) vs trauma-exposed PTSD (human); 
 # D=non-exposed vs trauma-exposed (no PTSD checked) (animal); E=non-exposed vs trauma-exposed PTSD (animal); F=trauma-exposed (no ptsd) vs trauma-exposed PTSD (animal)
```{r}
data %>% 
  filter(comparison !="B") %>%
  filter(phase !="E") %>%
  filter(valence !="T")%>% droplevels() ->data.phase.valence

# names(data)

#' Variable / level exclusion (see notes data prep file) 
#' NB Learning & memory of "Trauma" information are never measured in human (with behavioral tasks), therefor not an 'fair' comparison between animal & human..
#' Consider exclusion in 'analysis script'
 # data <- data %>% filter(valence != "T")%>% droplevels() ## Use as 'sensitivity check?'

#' NB extinction data is not available for all groups. Besides it is an specific for of fear learning..
#' Consider exclusion in 'analysis script'
#' 
 # data<- data %>% filter(phase != "E")%>% droplevels()
```

Other filters
```{r eval=FALSE, include=FALSE}
 #data <- data %>% filter(comparison %in% c("A","E"))%>% droplevels()
 # data <- data %>% filter(comparison %in% c("B","D"))%>% droplevels()
 # data <- data %>% filter(comparison %in% c("C","F"))%>% droplevels()
```

inspect data
```{r eval=FALSE, include=FALSE}
data.phase.valence %>% filter(subject.cat == "Animal", Valence_Grouped == "stress") %>% select(reference, measureID, phase, recode)
data.phase.valence %>% filter(subject.cat == "Animal", Valence_Grouped == "neutral") %>% select(reference, measureID, phase, recode, yi)

data.phase.valence %>% filter(subject.cat == "Human", Valence_Grouped == "stress") %>% select(reference, measureID, phase, recode)
data.phase.valence %>% filter(subject.cat == "Human", Valence_Grouped == "neutral") %>% select(reference, measureID, phase, recode)
```


## Split clinical and preclinical data
 Model 
 In explore_data script frequency of obervations in groups checked.. for now decided to analyse clinical & preclinical data separatly 

```{r}
# Clinical data 
data.phase.valence %>% filter(subject.cat =="Human") %>% droplevels() ->clinical
# Preclinical data 
data.phase.valence %>% filter(subject.cat =="Animal") %>% droplevels() ->preclinical
```


# **multilevel models**
code for posthoc Analyses + Plot:
```{r}
source("r/model_valence_phase.r")
```

## *Research Question 1: Learning and Memory of stressful and non-stressful information in PTSD patients*
```{r}
mod.H <- rma.mv(yi, vi,
                random = list(~1 | PMID, ~1 | idPTSD),  # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                mods   = ~phase:Valence_Grouped - 1,
                method = "REML",
                slab = clinical$reference,  # from old codes milou (change for author/year)
                data = clinical) # Similar effects with dat2 (trauma learning excluded)
summary(mod.H)



human<-TRACE_output(mod.H, title='Clinical Data', subtitle='PTSD patients' )  # volgorde contrasten klopt niet meer met code (emotional - stressvul)
human

# to save
jpeg(file="results/clinical.jpeg", height = 2000, width = 1500, res=300)
human[[2]]
dev.off()
```

## *Research Question 2: Learning and Memory of stressful and non-stressful information in animal models of PTSD*
```{r}
mod.A <- rma.mv(yi, vi,
                random = list(~1 | PMID, ~1 | idPTSD), # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                mods   = ~phase:Valence_Grouped - 1,  # NB only interaction term
                method = "REML",
                slab = preclinical$reference,  # from old codes milou (change for author/year)
                data = preclinical) # Similar effects with dat2 (trauma learning excluded)
summary(mod.A)

animal<-TRACE_output(mod.A, title='Preclinical Data', subtitle='animal models for PTSD')
animal

# to save
jpeg(file="results/preclinical.jpeg", height = 2000, width = 1500, res=300)
animal[[2]]
dev.off()
```

## **data presenation**
```{r}
# Show clincal & preclinical data in one figure.
plots<-ggarrange(
  human[[2]]
#  + ylim(-7.5,3.5)  # If you want y-axis the same for clinical and preclinical
  + rremove("x.text") + rremove("x.axis") + rremove("x.ticks") + rremove("xlab")
 + rremove("y.axis") + rremove("y.ticks"),
 
  animal[[2]]
# + ylim(-7.5,3.5)   # If you want y-axis the same for clinical and preclinical
 + rremove("x.text") + rremove("x.axis") + rremove("x.ticks") + rremove("xlab")
 + rremove("ylab") + rremove("y.axis") + rremove("y.ticks"),
  align = "v",
  legend="bottom",
  common.legend = T)

plots
```

## **safe results**
```{r}
# Save figure to jpeg.x
#ggsave(paste0("LearningMemoryPTSD_TRACE", date(),".jpg"), device="jpg", dpi = 500, height = 4, width = 6, limitsize = T )
ggsave(paste0("results/LearningMemoryPTSD_TRACE_NOinfluentials", date(),".jpg"), device="jpg", dpi = 300, height = 4, width = 6, limitsize = T )
#ggsave(paste0("LearningMemoryPTSD_TRACE_yshared", date(),".jpg"), device="jpg", dpi = 500, height = 4, width = 6, limitsize = T )
# ppt standard 4:3
```



# Sensitivity analysis

## study quality

### Clinical
```{r}
mod.H <- rma.mv(yi, vi,
                random = list(~1 | PMID, ~1 | idPTSD),  # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                mods   = ~phase:Valence_Grouped - 1,
                method = "REML",
                slab = clinical$reference,  # from old codes milou (change for author/year)
                data = clinical) # Similar effects with dat2 (trauma learning excluded)
summary(mod.H)
```

### Preclinical
```{r}
mod.A <- rma.mv(yi, vi,
                random = list(~1 | PMID, ~1 | idPTSD), # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                mods   = ~phase:Valence_Grouped - 1,  # NB only interaction term
                method = "REML",
                slab = preclinical$reference,  # from old codes milou (change for author/year)
                data = preclinical) # Similar effects with dat2 (trauma learning excluded)
summary(mod.A)
```



## Influential cases
 phase x valence meta-regression

without cases that were identified as influential &outlier -> for sensitivity analysis


### clinical
```{r}
#clinical.inf<-influentials_valence_phase(clinical)
 #saveRDS(clinical.inf, "processed_data/influentials.clinical.rds")
 readRDS("processed_data/influentials.clinical.rds")->clinical.inf
 
  # potential outlier and influential cases
clinical.inf[which(clinical.inf$outInf == 1),] %>% nrow()# 15 comparisons
clinical.inf[which(clinical.inf$outInf == 1),]%>% distinct(PMID) %>% nrow() # 7 papers

# # potential outliers
# clinical.inf[which(clinical.inf$potOut == 1),] %>% nrow()# 15 comparision 
# clinical.inf[which(clinical.inf$potOut == 1),]%>% distinct(PMID) %>% nrow()

# remove outliers
##  influential (Viechtbauer & Cheung) 
clinical.inf %>%
  filter(outInf != 1) %>%
  droplevels() -> clinical.noinfout
```


```{r}
mod.H.noinf <- rma.mv(yi, vi,
                random = list(~1 | PMID, ~1 | idPTSD),  # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                mods   = ~phase:Valence_Grouped - 1,
                method = "REML",
                slab = clinical.noinfout$reference,  # from old codes milou (change for author/year)
                data = clinical.noinfout) # Similar effects with dat2 (trauma learning excluded)

summary(mod.H.noinf)

```


### preclinical
```{r}
source("r/influentials_valence_phase.r")
#preclinical.inf<-influentials_valence_phase(preclinical)
 #saveRDS(preclinical.inf, "processed_data/influentials.preclinical.rds")
 readRDS("processed_data/influentials.preclinical.rds")->preclinical.inf
 
 # potential outlier and influential cases
preclinical.inf[which(preclinical.inf$outInf == 1),] %>% nrow() # 11 comparisons
preclinical.inf[which(preclinical.inf$outInf == 1),] %>% distinct(PMID) %>% nrow() # 4 papers

# preclinical.inf %>% filter(outInf == 1 & potOut==1) %>% nrow() # 11 comparisons
# preclinical.inf %>% filter(outInf == 1 & potOut==1) %>% distinct(PMID) %>% nrow() # 4 papers

# # potential outliers
# preclinical.inf[which(preclinical.inf$potOut == 1),] %>% nrow() # 28 comparisons
# preclinical.inf[which(preclinical.inf$potOut == 1),] %>% distinct(PMID) %>% nrow() # 14 papers
# preclinical.inf %>% filter(potOut!=1) #->data.sens

# remove outliers
##  influential (Viechtbauer & Cheung) 
# preclinical.inf %>%
#  filter(outInf != 1) %>%
# droplevels() -> preclinical.noinf # n=4 papers (11 comparison) excluded animal 

preclinical.inf %>%
 filter(outInf != 1) %>%  # potential outliers AND influential
   # filter(potOut!=1) %>%
droplevels() -> preclinical.noinfnoout
```

```{r}
mod.A.noinf <- rma.mv(yi, vi,
                random = list(~1 | PMID, ~1 | idPTSD), # valeria had each.. ik heb in oic meta PMID.. results ong same maar beetje anders -> volgens mij is PMID de bedoeling
                mods   = ~phase:Valence_Grouped - 1,  # NB only interaction term
                method = "REML",
                slab = preclinical.noinfnoout$reference,  # from old codes milou (change for author/year)
                data = preclinical.noinfnoout) # Similar effects with dat2 (trauma learning excluded)
summary(mod.A.noinf)
```




